---
title: "Merge eye-tracking data"
format: html
---

```{r}
library(tidyverse)
library(here)
library(assertthat)
```

Download data locally

```{r}

mb2_data <- osfr::osf_retrieve_node("p3txj")
files <- osfr::osf_ls_files(mb2_data)

PROCESSED_DATA_DIR = "processed_xy_data"

dir.create(here(PROCESSED_DATA_DIR), showWarnings = FALSE)

files |>
  mutate(idx = 1:n()) %>%
  base::split(.$idx) |>
  map(function(f) {
    print(f)
    osfr::osf_download(f, path = here(PROCESSED_DATA_DIR))
  })
```

Load local data

```{r}
cols <- c("lab_id", "participant_id", "media_name", 
          "x", "y", "t", "pupil_left", "pupil_right")

local_files <- dir(here("processed_xy_data"))

xy <- local_files |>
  map_df(function(x) {
    print(x)
    d <- read_csv(here("processed_xy_data",x),
                  col_types = list(
                    lab_id = col_character(),
                    participant_id = col_character(),
                    media_name = col_character(),
                    x = col_double(),
                    y = col_double(),
                    t = col_double(),
                    pupil_left = col_double(),
                    pupil_right = col_double()
                  ))
    
    # check that all columns are in the col list
    assert_that(all(cols %in% names(d)))
    
    # check that no extra cols
    assert_that(all(names(d) %in% cols))
    
    
    # check for milliseconds
    #assert_that(mean(diff(d$t),na.rm=TRUE) > 1 & 
    #            mean(diff(d$t), na.rm=TRUE) < 100)
    
    return(d)
  })
```
## Processing tasks that we will do centrally

Reconcile media names
Create trial numbers
Standardize media names
Zero times within trials
Resample times 
Clip XY outside of screen coordinates
Create/process AOIs
Standardize pupil sizes


```{r}

media_renamings <- read.csv(here('metadata','media_renaming.csv'))

media_names <- xy |>
  filter(!is.na(media_name)) |>
  mutate(media_name = tools::file_path_sans_ext(media_name)) %>% 
  group_by(media_name) %>%
  count()

media_events <- xy |>
  filter(!is.na(media_name)) |>
  group_by(lab_id, participant_id, media_name) |>
  count()
```









## Tests that we need on the merged data
Validate media orders with trial orders in the demographics file
Validate media names
Validate that the scale of timesteps is correct
