---
title: "MB2 exclusions"
format: html
---

Goal: implement exclusions, document numbers for exclusions in a separate CSV, and pass on a final datasaet. 

```{r}
library(tidyverse)
library(here)
library(assertthat)

source(here('helper','ensure_repo_structure.R'))
source(here('helper','exclusion_helper.R'))

load(here(INTERMEDIATE_FOLDER, INTERMEDIATE_005))
```

This process will be much easier if we create a field `unique_participant_id`.

```{r}
data_preprocessed <- data_preprocessed |>
  unite(col = "unique_participant_id",
        lab_id, participant_id, 
        remove = FALSE, sep = "-")
```


First trim toddlers 



> Of the initial sample (toddlers: N = XYZ, adults: N = XYZ), participants will be excluded from the main confirmatory analyses if 

> (1) they did not complete the full experiment, 

> (2) the toddler participants’ caregivers interfered with the procedure, e.g. by pointing at stimuli or talking to their child, 

> (3) the experimenter made an error during testing that was relevant to the procedure, 

> (4) technical problems occurred. The individual labs will determine whether and to which extent participant exclusion criteria 1-4 apply and add this information to the participant protocol sheet they provide. This set of exclusions will leave a total of XYZ toddlers and XYZ adults whose data will be analyzed. 

> Of these, participants will be excluded sequentially if 

> (5) their data is missing on more than one familiarization trial, or 

> (6) their data is missing on the first test trial. If multiple reasons for exclusion are applicable to a participant, the criteria will be assigned in the order above (for details on exclusions, see Supplemental Material).

> Our final dataset will consist of XYZ participants, with an overall exclusion rate of XYZ% (toddlers: XYZ%, adults: XYZ%). Tables 1 A. and B. show the distribution of included participants across labs, eye-tracking methods, and ages. A final sample of XYZ toddlers (XX% female) that will have been tested in XYZ labs (mean lab sample size = XYZ, SD = XYZ, range: XYZ) will be analyzed. The average age of toddlers in the final sample will be XYZ months (SD: XYZ, range: XYZ). The final sample size of included adults will be N = XYZ (XX% female), tested in XYZ labs (mean lab sample size = XYZ, SD = XYZ, range: XYZ). Their mean age will be XYZ years (SD: XYZ, range: XYZ).

```{r saving}
save(data_preprocessed, file = here(INTERMEDIATE_FOLDER, INTERMEDIATE_006))
```