---
title: "MB2 exclusions"
format: html
---

Goal: implement exclusions, document numbers for exclusions in a separate CSV, and pass on a final datasaet. 

```{r}
library(tidyverse)
library(here)
library(assertthat)
library(knitr)

source(here('helper','ensure_repo_structure.R'))
source(here('helper','exclusion_helper.R'))

load(here(INTERMEDIATE_FOLDER, INTERMEDIATE_005))
```

This process will be much easier if we create a field `unique_participant_id`.

```{r}
#this should be present once the pipeline is fully updated
data_preprocessed <- data_preprocessed |>
  unite(col = "unique_participant_id",
        lab_id, participant_id, 
        remove = FALSE, sep = "-")
```


First trim toddlers that are outside of age range. 

```{r}
# this needs to be filled in after we have age in the preprocessed file.
```




> Of the initial sample (toddlers: N = XYZ, adults: N = XYZ), participants will be excluded from the main confirmatory analyses if 

> (1) they did not complete the full experiment, 

```{r}
# data_after_exclusions <- exclude_by(d = data_preprocessed, 
#                                     col = 
```



> (2) the toddler participants’ caregivers interfered with the procedure, e.g. by pointing at stimuli or talking to their child, 


```{r}
# data_after_exclusions <- exclude_by(d = data_preprocessed, 
#                                     col = 
```


> (3) the experimenter made an error during testing that was relevant to the procedure, 


```{r}
# data_after_exclusions <- exclude_by(d = data_preprocessed, 
#                                     col = 
```


> (4) technical problems occurred. The individual labs will determine whether and to which extent participant exclusion criteria 1-4 apply and add this information to the participant protocol sheet they provide. This set of exclusions will leave a total of XYZ toddlers and XYZ adults whose data will be analyzed. 

```{r}
# data_after_exclusions <- exclude_by(d = data_preprocessed, 
#                                     col = 
```

# Individual Trial Exclusions

## Sufficient Looking Data per Trial

"We will exclude individual trials if more than 50% of the gaze data is missing (defined as off-screen or unavailable point of gaze during the whole trial, not just the anticipatory period)." (p. 33 Stage 1 Registered Report)

```{r}
# summarize by participant, trial and condition
summarized_valid_looks <- data_preprocessed %>%
  #define a valid point of gaze
  #we define a valid point of gaze as requiring both a valid x-coordinate and a valid y-coordinate
  mutate(
    valid_xy_look_type = case_when(
      !is.na(x_screen) & !is.na(y_screen) ~ "both x and y are valid",
      !is.na(x_screen) & is.na(y_screen) ~ "x is valid but not y",
      is.na(x_screen) & !is.na(y_screen) ~ "y is valid but not x",
      is.na(x_screen) & is.na(y_screen) ~ "neither x nor y are valid",
      TRUE ~ "check for error"
    )
  ) %>%
  mutate(
    valid_xy_look = ifelse(valid_xy_look_type == "both x and y are valid",1,0)
  ) %>%
  #only focus on familiarization and test trials
  filter(condition %in% c("familiarization", "ignorance", "knowledge")) %>%
  group_by(unique_participant_id,lab_id,age_cohort,condition,participant_id,participant_trial_id,trial_num) %>%
  summarize(
    total_frames=n(),
    total_valid_looks = sum(valid_xy_look),
    prop_valid_looks = total_valid_looks / total_frames
  )
```

Inspect the resulting valid looking data

```{r}
hist(summarized_valid_looks$prop_valid_looks)

ggplot(summarized_valid_looks, aes(prop_valid_looks,fill=age_cohort))+
  geom_histogram()+
  facet_wrap(~age_cohort+condition)
```

Exclude trials that do not meet the 50% valid looking criterion

```{r}
summarized_valid_looks <- summarized_valid_looks %>%
  mutate(
    valid_looking_trial = case_when(
      prop_valid_looks >= 0.5 ~ 1,
      TRUE ~ 0
    )) %>%
  mutate(
    trial_error = case_when(
      valid_looking_trial == 0 ~ "yes",
      TRUE ~ "no"
    ),
    trial_error_type = case_when(
      valid_looking_trial == 0 ~ "insufficient valid looking data",
      TRUE ~ NA
    )
  )

# inspect trial errors by age cohort and condition
summarized_valid_looks %>%
  group_by(age_cohort,condition,trial_num) %>%
  summarize(
    total_trials = n(),
    valid_trials = sum(valid_looking_trial),
    prop_valid_trials = valid_trials/total_trials
  )
```

Join back in the information about trial errors into the overall data

```{r}
data_preprocessed <- data_preprocessed %>%
  left_join(summarized_valid_looks)
```

# Trial-based Exclusions

## Sufficient Valid Familiarization Trials

> Of these, participants will be excluded sequentially if (5) their data is missing on more than one familiarization trial, or 

Summarize the number of valid familiarization trials by participant.

```{r}
summarized_valid_familiarization_trials <- data_preprocessed %>%
  filter(condition == "familiarization") %>%
  filter(trial_error == "no") %>%
  distinct(unique_participant_id,lab_id,age_cohort,participant_id,participant_trial_id,trial_num) %>%
  group_by(unique_participant_id,lab_id,age_cohort,participant_id) %>%
  summarize(
    total_valid_fam_trials = n()
  )

#inspect
ggplot(summarized_valid_familiarization_trials, aes(total_valid_fam_trials,fill=age_cohort))+
  geom_histogram()+
  facet_wrap(~age_cohort)

#participants are excluded if insufficient valid familiarization trials are available
summarized_valid_familiarization_trials <- summarized_valid_familiarization_trials %>%
  mutate(
    sufficient_fam_trials = ifelse(total_valid_fam_trials>=3,1,0)
  )

#join back in to main data
data_preprocessed <- data_preprocessed %>%
  left_join(summarized_valid_familiarization_trials)
```

## Valid First Test Trial

> (6) their data is missing on the first test trial. If multiple reasons for exclusion are applicable to a participant, the criteria will be assigned in the order above (for details on exclusions, see Supplemental Material).

Identify participants without the first test trial

```{r}
# identify valid and invalid first test trials
summarized_valid_first_test_trials <- data_preprocessed %>%
  filter(condition %in% c("ignorance","knowledge")) %>%
  # check this, need to make sure this is a robust way of identifying the first test trial
  filter(trial_num==5) %>%
  distinct(unique_participant_id,lab_id,age_cohort,condition,participant_id,participant_trial_id,trial_num,trial_error) %>%
  mutate(
    valid_first_test_trial = case_when(
      trial_error == "yes" ~ 0,
      trial_error == "no" ~ 1,
      TRUE ~ NA
    )
  ) %>%
  #remove columns that vary within participants, to make joining at the participant level possible
  select(-condition, -participant_trial_id,-trial_num)

#join back in to main data
data_preprocessed <- data_preprocessed %>%
  left_join(summarized_valid_first_test_trials)
```

## Overall Trial-based Exclusions

```{r}
participant_trial_errors <- data_preprocessed %>%
  mutate(
    trial_based_error = case_when(
      #step 5 (familiarization)
      sufficient_fam_trials == 0 ~ "yes",
      #step 6 (first test trial)
      valid_first_test_trial == 0 ~ "yes",
      TRUE ~ "no"
    ),
    trial_based_error_type = case_when(
      sufficient_fam_trials == 0 ~ "5",
      valid_first_test_trial == 0 ~ "6",
      TRUE ~ NA
    )
  )
  
```

## Overview

```{r}
overview_trial_based_errors <- data_preprocessed %>%
  distinct(unique_participant_id,lab_id,age_cohort,participant_id,trial_based_error,trial_based_error_type) %>%
  group_by(age_cohort) %>%
  summarize(
    total_N = n(),
    trial_error_exclusions = sum(trial_based_error=="yes"),
    prop_excluded = trial_error_exclusions / total_N
  )

overview_trial_based_errors %>%
  knitr::kable()

```

> TO DO: spit out overview of trial-based exclusions and pass a dataset with trial-based exclusions incorporated on to the next processing step


> Our final dataset will consist of XYZ participants, with an overall exclusion rate of XYZ% (toddlers: XYZ%, adults: XYZ%). Tables 1 A. and B. show the distribution of included participants across labs, eye-tracking methods, and ages. A final sample of XYZ toddlers (XX% female) that will have been tested in XYZ labs (mean lab sample size = XYZ, SD = XYZ, range: XYZ) will be analyzed. The average age of toddlers in the final sample will be XYZ months (SD: XYZ, range: XYZ). The final sample size of included adults will be N = XYZ (XX% female), tested in XYZ labs (mean lab sample size = XYZ, SD = XYZ, range: XYZ). Their mean age will be XYZ years (SD: XYZ, range: XYZ).

```{r saving}
save(data_preprocessed, file = here(INTERMEDIATE_FOLDER, INTERMEDIATE_006))
```