---
title: "Exploratory analyses"
format: html
---

```{r}
library(tidyverse)
library(here)
library(assertthat)
library(ggbeeswarm)
library(gghalves)
library(cowplot)
library(patchwork)
library(brms)
library(tidybayes)
library(knitr)
library(corrr)
library(ggpubr)

source(here('helper','ensure_repo_structure.R'))
plot_path <- here("plots")
paper_path <- here("paper")

load(here(INTERMEDIATE_FOLDER, INTERMEDIATE_002B))
load(here(INTERMEDIATE_FOLDER, INTERMEDIATE_006))
```

# Load data

```{r}
# Load all .rds files
# List all RDS files in the results folder
rds_files <- list.files(RESULTS_FOLDER, pattern = "\\.rds$", full.names = TRUE)

# Load each RDS file as a separate variable in the global environment
for (file in rds_files) {
  rds_name <- tools::file_path_sans_ext(basename(file))
  assign(rds_name, readRDS(file))
}
```

Splitting the data into familiarization data and test data.

```{r}
fam_data <- data_preprocessed_post_exclusions %>%
  filter(condition %in% c("familiarization"))

test_data <- data_preprocessed_post_exclusions %>%
  filter(condition %in% c("knowledge","ignorance"))
```

# Exploratory analyses

## 1. Spill-over:

Spill-over: we will analyze within-participants data from the second test trial that participants saw, using exploratory models to assess whether (1) findings are consistent when both trials are included (overall condition effect), (2) whether effects are magnified or diminished on the second trial (order main effect), and (3) whether there is evidence of “spillover” - dependency in anticipation on the second trial depending on what the first trial is (condition x order interaction effect).

## 1.a.Spill-over Analysis

### Summarize all test data

```{r}
#now summarize test data for each trial
summarize_participant_test_both_trials <- test_data %>%
  group_by(lab_id,age_cohort,age_mo,age_years_n,participant_lab_id,participant_id,participant_trial_id,trial_num,trial_file_name,
           bear_not_visible_ms,point_of_disambiguation,video_duration_ms,condition, data_type) %>%
  #filter to relevant anticipatory window
  # based on current format, t_norm == 0 is the point of disambiguation
  # so we want the 4000 ms leading up, minus 120 ms of saccade/ planning time
  filter(t_norm<=120 & t_norm>=-3880) %>%
  mutate(
    aoi_diff = c(0,diff(as.numeric(as.factor(aoi))))
  ) %>%
  summarize(
    t_min=min(t_norm),
    t_max=max(t_norm),
    sum_target_general = sum(aoi=="target_general",na.rm=T),
    sum_distractor_general = sum(aoi=="distractor_general",na.rm=T),
    prop_general = sum_target_general/(sum_target_general+sum_distractor_general),
    sum_target_exit = sum(aoi=="target_exit",na.rm=T),
    sum_distractor_exit = sum(aoi=="distractor_exit",na.rm=T),
    prop_exit = sum_target_exit/(sum_target_exit+sum_distractor_exit),
    N_general = sum_target_general+sum_distractor_general,
    N_exit = sum_target_exit+sum_distractor_exit
  ) %>%
  ungroup() %>%
  #center age, condition, and method
  mutate(
    age_mo_c = age_mo - mean(age_mo,na.rm=TRUE),
    condition_c = case_when(
      condition=="knowledge" ~ -0.5,
      condition=="ignorance" ~ 0.5),
    method_c = case_when( 
      data_type=="web-based" ~ -0.5,
      data_type=="in-lab" ~ 0.5)
  ) %>%
  mutate(
    test_trial_num = trial_num-4
  )


```

### Overall Plots

First look at the proportional looking measures, focusing on the target exit during the anticipatory window.

```{r}
#plot average proportion looking
overall_p_test_both <- ggplot(summarize_participant_test_both_trials, aes(x=condition, y=prop_exit,color=condition))+
  #geom_violin()+
  #geom_boxplot()+
  geom_beeswarm(alpha=0.2,cex=0.2)+
  geom_half_violin(data=filter(summarize_participant_test_both_trials,condition=="ignorance"),aes(fill=condition),side="l",nudge=0.3,width=0.4,alpha=0.2)+
  geom_half_violin(data=filter(summarize_participant_test_both_trials,condition=="knowledge"),aes(fill=condition),side="r",nudge=0.3,width=0.4,alpha=0.2)+
  geom_half_boxplot(data=filter(summarize_participant_test_both_trials,condition=="ignorance"),side="l",nudge=0.15,width=0.4,errorbar.draw=F)+
  geom_half_boxplot(data=filter(summarize_participant_test_both_trials,condition=="knowledge"),side="r",nudge=0.15,width=0.4,errorbar.draw=F)+
  stat_summary(fun.data="mean_cl_boot",size=1,color="black")+
  geom_hline(yintercept=0.5,linetype="dashed")+
  theme_cowplot()+
  scale_color_brewer(palette="Set1")+
  scale_fill_brewer(palette="Set1")+
  facet_wrap(age_cohort~test_trial_num)+
  theme(legend.position="none")+
  #ggtitle("Test")+
  theme(plot.title = element_text(hjust= 0.5, face="bold"))+
  ylab("Proportion Looking to Exit\n(Anticipatory Window, Both Trials)")
overall_p_test_both
ggsave(here(plot_path,"overall_proportion_both_trials_target_exit_looking.png"),bg="white",width=9,height=9)
```

Plot the effect by age

```{r}
kid_prop_by_age_both <- ggplot(filter(summarize_participant_test_both_trials,N_exit>=5&age_cohort=="toddlers"),aes(x=age_mo,y=prop_exit,color=condition))+
  geom_hline(yintercept=0.5, linetype="dashed")+
  geom_point(alpha=0.4)+
  geom_smooth(method="lm")+
  xlab("Age (in months)")+
  ylab("Proportion Looking to Exit\n(Anticipatory Window, Both Trials)")+
  theme_cowplot()+
  facet_wrap(~test_trial_num)+
  scale_color_brewer(palette="Set1")+
  scale_fill_brewer(palette="Set1")
kid_prop_by_age_both
ggsave(here(plot_path,"kids_proportion_both_trials_target_exit_looking_by_age.png"),bg="white", width = 9, height = 6)
```

### Summary Statistics

```{r}
summarize_test_aoi_both <- summarize_participant_test_both_trials %>%
  group_by(age_cohort,condition,trial_num,test_trial_num) %>%
  summarize(
    participant_num=sum(!is.na(prop_exit)),
    mean_target_looking=mean(prop_exit,na.rm=T),
    sd_target_looking=sd(prop_exit,na.rm=T),
     t_test = list(broom::tidy(t.test(prop_exit, alternative = "two.sided", mu=0.5)))) %>%
  mutate(
    #95% CIs
    lower_ci_target_looking = mean_target_looking - qt(1 - (0.05 / 2), participant_num - 1) * sd_target_looking/sqrt(participant_num),
    upper_ci_target_looking = mean_target_looking + qt(1 - (0.05 / 2), participant_num - 1) * sd_target_looking/sqrt(participant_num),
    #mean_target_looking_general = mean(prop_general, na.rm=T),
   # sd_target_looking_general=sd(prop_general,na.rm=T),
    lower_ci_target_looking_general = mean_target_looking - qt(1 - (0.05 / 2), participant_num - 1) * sd_target_looking/sqrt(participant_num),
    upper_ci_target_looking_general = mean_target_looking + qt(1 - (0.05 / 2), participant_num - 1) * sd_target_looking/sqrt(participant_num),
    p.value = purrr::map(t_test, ~select(.x, c('p.value', 'parameter','statistic')))
  ) %>%
  select(-t_test) %>%
  unnest(p.value) %>%
  rename(
    tval=statistic,
    df=parameter
  )
  

summarize_test_aoi_both %>%
  knitr::kable()

saveRDS(summarize_test_aoi_both, file = here(RESULTS_FOLDER,"summarize_test_aoi_both.rds"))
```

### Main Model

Fitting the main Bayesian hierarchical model testing the effect of condition (ignorance vs. knowledge) on first-trial proportion target looking during the anticipatory window.

#### Toddlers

## MZ: NEED TO DISCUSS MODEL STRUCTURE HERE ##

```{r}
#set the prior
priors <-c(
  set_prior("uniform(0, 1)", lb=0,ub=1,class = "Intercept"), #uniform distribution for intercept
  set_prior("normal(0, .1)", class = "b"), # normal distribution for fixed-effect coefficients
  set_prior("normal(0, .05)", class = "sd"), #normal distribution for sd/ random effects
  set_prior("lkj(2)", class = "L")) # lkj distribution for covariance matrix/Cholesky Factor?

bm_aoi_toddlers_both <- brm(prop_exit ~ 1+condition_c*age_mo_c+(1+condition_c|participant_lab_id)+(1+condition_c*age_mo_c|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_both_trials,age_cohort=="toddlers"),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_toddlers_both)
prior_summary(bm_aoi_toddlers_both)

saveRDS(bm_aoi_toddlers_both, file = here(RESULTS_FOLDER,"bm_aoi_toddlers_both.rds"))
```

Summarize outcomes

```{r}
#get_variables(bm_aoi_toddlers)
#get main coefficient estimate and HDI
bm_aoi_toddlers_both %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_both %>%
  spread_draws(b_age_mo_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_both %>%
  spread_draws(`b_condition_c:age_mo_c`, sigma) %>%
  mean_hdi(.width = 0.95)
```

Visualize model coefficients

```{r}
bm_aoi_toddlers_both %>%
  spread_draws(b_condition_c,b_age_mo_c,`b_condition_c:age_mo_c`, sigma) %>%
  pivot_longer(cols = starts_with("b_"), names_to = "coefficient", values_to = "b") %>%
  ggplot(aes(x = coefficient,y=b)) +
  stat_halfeye()+
  geom_hline(yintercept=0,linetype="dashed")+
  theme_cowplot()+
  scale_x_discrete(limits=c("b_condition_c:age_mo_c","b_age_mo_c","b_condition_c"),labels=c("Condition x Age","Age","Condition"))+
  ylab("Model Coefficient Estimate")+
  xlab("Model Predictor")+
  coord_flip()
ggsave(here(plot_path,"test_toddlers_model_coefficients_both.png"),bg="white",width=9,height=6)
```


Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_toddlers_both <- hypothesis(bm_aoi_toddlers_both, "condition_c = 0", class="b")
h_aoi_toddlers_both
plot(h_aoi_toddlers_both)
# evidence in favor of condition being different from zero
1/h_aoi_toddlers_both$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_toddlers_both <-  update(bm_aoi_toddlers_both, formula = ~ .-condition_c)
summary(null_aoi_toddlers_both)
brms::bayes_factor(bm_aoi_toddlers_both, null_aoi_toddlers_both)
```


#### Adults

## MZ: NEED TO DISCUSS MODEL STRUCTURE HERE ##

```{r}
bm_aoi_adults_both <- brm(prop_exit ~ 1+condition_c+(1+condition_c|lab_id)+(1+condition_c|participant_lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_both_trials,age_cohort=="adults"),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_adults_both)

saveRDS(bm_aoi_adults_both, file = here(RESULTS_FOLDER,"bm_aoi_adults_both.rds"))
```

```{r}
#get main coefficient estimate and HDI
bm_aoi_adults_both %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)
```

Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_adults_both <- hypothesis(bm_aoi_adults_both, "condition_c = 0")
h_aoi_adults_both 
plot(h_aoi_adults_both)
# evidence in favor of condition being different from zero
1/h_aoi_adults_both$hypothesis$Evid.Ratio
```
Visualize model coefficients

```{r}
bm_aoi_adults_both %>%
  spread_draws(b_condition_c, sigma) %>%
  pivot_longer(cols = starts_with("b_"), names_to = "coefficient", values_to = "b") %>%
  ggplot(aes(x = coefficient,y=b)) +
  stat_halfeye()+
  geom_hline(yintercept=0,linetype="dashed")+
  theme_cowplot()+
  scale_x_discrete(limits=c("b_condition_c"),labels=c("Condition"))+
  ylab("Model Coefficient Estimate")+
  xlab("Model Predictor")+
  coord_flip()
ggsave(here(plot_path,"test_adults_model_coefficients_both.png"),bg="white",width=9,height=6)
```

Alternate Bayes factor approach

```{r}
null_aoi_adults_both <-  update(bm_aoi_adults_both, formula = ~ .-condition_c)
summary(null_aoi_adults_both)
brms::bayes_factor(bm_aoi_adults_both, null_aoi_adults_both)
```

## 1.b. whether effects are magnified or diminished on the second trial (order main effect), and (3) whether there is evidence of “spillover” - dependency in anticipation on the second trial depending on what the first trial is (condition x order interaction effect)

## MZ this needs further discussion - I'm not sure how to parse what is in the preregistration, but my reading is that at least for (2), and perhaps for (3), we are asking about a trial number by condition effect (not the "order" as defined here)

```{r}
# create order variable
summarize_participant_test_both_trials <- summarize_participant_test_both_trials %>% 
  ungroup() %>%
  arrange(participant_lab_id,trial_num,test_trial_num) %>%
  group_by(participant_lab_id) %>%
  mutate(conditions = paste0(condition, collapse = "_")) %>%
  ungroup() %>%
 mutate(test_trial=case_when(
     trial_num==5 ~ 1, 
     trial_num==6 ~ 2,
     TRUE ~ NA))
```

### Main Model

Fitting the main Bayesian hierarchical model testing the effect of condition (ignorance vs. knowledge) and order on proportion target looking during the anticipatory window.

#### Toddlers

```{r}
#set the prior
priors <-c(
  set_prior("uniform(0, 1)", lb=0,ub=1,class = "Intercept"), #uniform distribution for intercept
  set_prior("normal(0, .1)", class = "b"), # normal distribution for fixed-effect coefficients
  set_prior("normal(0, .05)", class = "sd"), #normal distribution for sd/ random effects
  set_prior("lkj(2)", class = "L")) # lkj distribution for covariance matrix/Cholesky Factor?

bm_aoi_toddlers_both_order <- brm(prop_exit ~ 1+condition_c*test_trial_num+(1+condition_c*test_trial_num|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_both_trials, age_cohort=="toddlers"),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_toddlers_both_order)
prior_summary(bm_aoi_toddlers_both_order)

saveRDS(bm_aoi_toddlers_both_order, file = here(RESULTS_FOLDER,"bm_aoi_toddlers_both_order.rds"))
```

Summarize outcomes

```{r}
#get_variables(bm_aoi_toddlers)
#get main coefficient estimate and HDI
bm_aoi_toddlers_both_order %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_both_order %>%
  spread_draws(b_test_trial_num, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_both_order %>%
  spread_draws(`b_condition_c:test_trial_num`, sigma) %>%
  mean_hdi(.width = 0.95)
```

Visualize model coefficients

```{r}
bm_aoi_toddlers_both_order %>%
  spread_draws(b_condition_c,b_test_trial_num,`b_condition_c:test_trial_num`, sigma) %>%
  pivot_longer(cols = starts_with("b_"), names_to = "coefficient", values_to = "b") %>%
  ggplot(aes(x = coefficient,y=b)) +
  stat_halfeye()+
  geom_hline(yintercept=0,linetype="dashed")+
  theme_cowplot()+
  scale_x_discrete(limits=c("b_condition_c:test_trial_num","b_test_trial_num","b_condition_c"),labels=c("Condition x Test Trial","Test Trial","Condition"))+
  ylab("Model Coefficient Estimate")+
  xlab("Model Predictor")+
  coord_flip()
ggsave(here(plot_path,"test_toddlers_model_coefficients_both_order.png"),bg="white",width=9,height=6)
```


Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_toddlers_both_order <- hypothesis(bm_aoi_toddlers_both_order, "test_trial_num = 0", class="b")
h_aoi_toddlers_both_order
plot(h_aoi_toddlers_both_order)
# evidence in favor of condition being different from zero
1/h_aoi_toddlers_both_order$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_toddlers_both_order <-  update(bm_aoi_toddlers_both_order, formula = ~ .-test_trial_num)
summary(null_aoi_toddlers_both_order)
brms::bayes_factor(bm_aoi_toddlers_both_order, null_aoi_toddlers_both_order)
```

#### Adults

```{r}
bm_aoi_adults_both_order <- brm(prop_exit ~ 1+condition_c*test_trial_num+(1+condition_c*test_trial_num|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_both_trials,age_cohort=="adults"),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_adults_both_order)

saveRDS(bm_aoi_adults_both_order, file = here(RESULTS_FOLDER,"bm_aoi_adults_both_order.rds"))
```


```{r}
#get main coefficient estimate and HDI
bm_aoi_adults_both_order %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_adults_both_order %>%
  spread_draws(b_test_trial_num, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_adults_both_order %>%
  spread_draws(`b_condition_c:test_trial_num`, sigma) %>%
  mean_hdi(.width = 0.95)
```
Visualize model coefficients

```{r}
bm_aoi_adults_both_order %>%
  spread_draws(b_condition_c,b_test_trial_num,`b_condition_c:test_trial_num`, sigma) %>%
  pivot_longer(cols = starts_with("b_"), names_to = "coefficient", values_to = "b") %>%
  ggplot(aes(x = coefficient,y=b)) +
  stat_halfeye()+
  geom_hline(yintercept=0,linetype="dashed")+
  theme_cowplot()+
  scale_x_discrete(limits=c("b_condition_c:test_trial_num","b_test_trial_num","b_condition_c"),labels=c("Condition x Test Trial","Test Trial","Condition"))+
  ylab("Model Coefficient Estimate")+
  xlab("Model Predictor")+
  coord_flip()
ggsave(here(plot_path,"test_adults_model_coefficients_both_order.png"),bg="white",width=9,height=6)
```


Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_adults_both_order <- hypothesis(bm_aoi_adults_both_order, "test_trial_num = 0")
h_aoi_adults_both_order 
plot(h_aoi_adults_both_order)
# evidence in favor of condition being different from zero
1/h_aoi_adults_both_order$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_adults_both_order <-  update(bm_aoi_adults_both_order, formula = ~ .-test_trial_num)
summary(null_aoi_adults_both_order)
brms::bayes_factor(bm_aoi_adults_both_order, null_aoi_adults_both_order)
```

## 2. Connections between familiarization and test

We will explore whether condition differences vary for participants who show higher rates of anticipation during the four familiarization trials. For example, we might group participants according to whether they did or did not show correct AL at the end of the familiarization phase, defined as overall longer looking at the correct AOI than the incorrect AOI on average in trials 3 and 4 of the familiarization phase.

### 2.a. Only anticipators on final familiarization trial

```{r}
#first, find the participants who anticipate correctly on the last trial
summarize_first_looks_fam_trials <- d_anticipatory_fam %>%
  group_by(age_cohort,participant_lab_id,lab_id,participant_id,condition,trial_num) %>%
  summarize(
    prop_correct_first_look = mean(first_look =="target_exit"),
    average_rt = mean(first_look_rt),
    average_rt_correct = mean(first_look_rt[first_look =="target_exit"])
  )
correct_first_looks_final_fam_trial <- summarize_first_looks_fam_trials %>%
  filter(!is.na(prop_correct_first_look)&trial_num==4) %>%
  ungroup() %>%
  select(age_cohort,lab_id, participant_id, participant_lab_id,prop_correct_first_look) %>%
  rename(correct_first_look_final_fam_trial=prop_correct_first_look)

#join in to test trial
summarize_participant_test_first_trial <- summarize_participant_test_first_trial %>%
  left_join(correct_first_looks_final_fam_trial)
summarize_participant_test_first_look_first_trial <- summarize_participant_test_first_look_first_trial %>%
  left_join(correct_first_looks_final_fam_trial)

# overall plot
#plot average proportion looking
overall_p_correct_final_fam_trial <- ggplot(filter(summarize_participant_test_first_trial,correct_first_look_final_fam_trial==1), aes(x=condition, y=prop_exit,color=condition))+
  #geom_violin()+
  #geom_boxplot()+
  geom_beeswarm(alpha=0.2,cex=0.5)+
  geom_half_violin(data=filter(summarize_participant_test_first_trial,correct_first_look_final_fam_trial==1&condition=="ignorance"),aes(fill=condition),side="l",nudge=0.3,width=0.4,alpha=0.2)+
  geom_half_violin(data=filter(summarize_participant_test_first_trial,correct_first_look_final_fam_trial==1&condition=="knowledge"),aes(fill=condition),side="r",nudge=0.3,width=0.4,alpha=0.2)+
  geom_half_boxplot(data=filter(summarize_participant_test_first_trial,correct_first_look_final_fam_trial==1&condition=="ignorance"),side="l",nudge=0.15,width=0.4,errorbar.draw=F)+
  geom_half_boxplot(data=filter(summarize_participant_test_first_trial,correct_first_look_final_fam_trial==1&condition=="knowledge"),side="r",nudge=0.15,width=0.4,errorbar.draw=F)+
  stat_summary(fun.data="mean_cl_boot",size=1.5,color="black")+
  geom_hline(yintercept=0.5,linetype="dashed")+
  theme_cowplot()+
  scale_color_brewer(palette="Set1")+
  scale_fill_brewer(palette="Set1")+
  facet_wrap(~age_cohort)+
  theme(legend.position="none")+
  ylab("Proportion Looking to Exit\n(Anticipatory Window, First Trial)")
overall_p_correct_final_fam_trial
ggsave(here(plot_path,"overall_proportion_first_trial_target_exit_looking_correct_final_fam_first_look.png"),bg="white",width=9,height=6)
```

#### Summary Statistics

```{r}
summarize_test_aoi_correct_final_fam_trial <- summarize_participant_test_first_trial %>%
  filter(correct_first_look_final_fam_trial==1) %>%
  group_by(age_cohort,condition) %>%
  summarize(
    participant_num=sum(!is.na(prop_exit)),
    mean_target_looking=mean(prop_exit,na.rm=T),
    sd_target_looking=sd(prop_exit,na.rm=T),
    mean_target_looking_general = mean(prop_general, na.rm=T),
    sd_target_looking_general=sd(prop_general,na.rm=T),
  )

summarize_test_aoi_correct_final_fam_trial %>%
  knitr::kable()
```

#### Main Model

Fitting the main Bayesian hierarchical model testing the effect of condition (ignorance vs. knowledge) on first-trial proportion target looking during the anticipatory window for only those participants who anticipated correctly during the last familiarization trial (trial 4, first look to target).

##### Toddlers

```{r}
#set the prior
priors <-c(
  set_prior("uniform(0, 1)", lb=0,ub=1,class = "Intercept"), #uniform distribution for intercept
  set_prior("normal(0, .1)", class = "b"), # normal distribution for fixed-effect coefficients
  set_prior("normal(0, .05)", class = "sd"), #normal distribution for sd/ random effects
  set_prior("lkj(2)", class = "L")) # lkj distribution for covariance matrix/Cholesky Factor?

bm_aoi_toddlers_correct_final_fam_trial <- brm(prop_exit ~ 1+condition_c*age_mo_c+(1+condition_c*age_mo_c|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_first_trial,age_cohort=="toddlers"&correct_first_look_final_fam_trial==1),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_toddlers_correct_final_fam_trial)

saveRDS(bm_aoi_toddlers_correct_final_fam_trial, file = here(RESULTS_FOLDER,"bm_aoi_toddlers_correct_final_fam_trial.rds"))
```

Summarize outcomes

```{r}
#get_variables(bm_aoi_toddlers)
#get main coefficient estimate and HDI
bm_aoi_toddlers_correct_final_fam_trial %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_correct_final_fam_trial %>%
  spread_draws(b_age_mo_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_correct_final_fam_trial %>%
  spread_draws(`b_condition_c:age_mo_c`, sigma) %>%
  mean_hdi(.width = 0.95)
```

Visualize model coefficients

```{r}
bm_aoi_toddlers_correct_final_fam_trial %>%
  spread_draws(b_condition_c,b_age_mo_c,`b_condition_c:age_mo_c`, sigma) %>%
  pivot_longer(cols = starts_with("b_"), names_to = "coefficient", values_to = "b") %>%
  ggplot(aes(x = coefficient,y=b)) +
  stat_halfeye()+
  geom_hline(yintercept=0,linetype="dashed")+
  theme_cowplot()+
  scale_x_discrete(limits=c("b_condition_c:age_mo_c","b_age_mo_c","b_condition_c"),labels=c("Condition x Age","Age","Condition"))+
  ylab("Model Coefficient Estimate")+
  xlab("Model Predictor")+
  coord_flip()
ggsave(here(plot_path,"test_toddlers_model_coefficients_correct_final_fam_trial.png"),bg="white",width=9,height=6)
```


Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_toddlers_correct_final_fam_trial <- hypothesis(bm_aoi_toddlers_correct_final_fam_trial, "condition_c = 0", class="b")
h_aoi_toddlers_correct_final_fam_trial
plot(h_aoi_toddlers_correct_final_fam_trial)
# evidence in favor of condition being different from zero
1/h_aoi_toddlers_correct_final_fam_trial$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_toddlers_correct_final_fam_trial <-  update(bm_aoi_toddlers_correct_final_fam_trial, formula = ~ .-condition_c)
summary(null_aoi_toddlers_correct_final_fam_trial)
brms::bayes_factor(bm_aoi_toddlers_correct_final_fam_trial, null_aoi_toddlers_correct_final_fam_trial)
```
##### Adults

```{r}
bm_aoi_adults_correct_final_fam_trial <- brm(prop_exit ~ 1+condition_c+(1+condition_c|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_first_trial,age_cohort=="adults"&correct_first_look_final_fam_trial==1),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_adults_correct_final_fam_trial)

saveRDS(bm_aoi_adults_correct_final_fam_trial, file = here(RESULTS_FOLDER,"bm_aoi_adults_correct_final_fam_trial.rds"))
```

```{r}
#get main coefficient estimate and HDI
bm_aoi_adults_correct_final_fam_trial %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)
```

Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_adults_correct_final_fam_trial <- hypothesis(bm_aoi_adults_correct_final_fam_trial, "condition_c = 0", class="b")
h_aoi_adults_correct_final_fam_trial
plot(h_aoi_adults_correct_final_fam_trial)
# evidence in favor of condition being different from zero
1/h_aoi_adults_correct_final_fam_trial$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_adults_correct_final_fam_trial <-  update(bm_aoi_adults_correct_final_fam_trial, formula = ~ .-condition_c)
summary(null_aoi_adults_correct_final_fam_trial)
brms::bayes_factor(bm_aoi_adults_correct_final_fam_trial, null_aoi_adults_correct_final_fam_trial)
```

### 2.b. Only >50% looking to target during familiarization trials

#### Plot

```{r}
#join overall familiarization looking in to test trial
summarize_participant_test_first_trial <- summarize_participant_test_first_trial %>%
  left_join(summarize_participant_familiarization_overall)

# overall plot
#plot average proportion looking
overall_p_sufficient_fam_prop_looking <- ggplot(filter(summarize_participant_test_first_trial,fam_prop_exit>0.5), aes(x=condition, y=prop_exit,color=condition))+
  #geom_violin()+
  #geom_boxplot()+
  geom_beeswarm(alpha=0.2,cex=0.5)+
  geom_half_violin(data=filter(summarize_participant_test_first_trial,fam_prop_exit>0.5&condition=="ignorance"),aes(fill=condition),side="l",nudge=0.3,width=0.4,alpha=0.2)+
  geom_half_violin(data=filter(summarize_participant_test_first_trial,fam_prop_exit>0.5&condition=="knowledge"),aes(fill=condition),side="r",nudge=0.3,width=0.4,alpha=0.2)+
  geom_half_boxplot(data=filter(summarize_participant_test_first_trial,fam_prop_exit>0.5&condition=="ignorance"),side="l",nudge=0.15,width=0.4,errorbar.draw=F)+
  geom_half_boxplot(data=filter(summarize_participant_test_first_trial,fam_prop_exit>0.5&condition=="knowledge"),side="r",nudge=0.15,width=0.4,errorbar.draw=F)+
  stat_summary(fun.data="mean_cl_boot",size=1.5,color="black")+
  geom_hline(yintercept=0.5,linetype="dashed")+
  theme_cowplot()+
  scale_color_brewer(palette="Set1")+
  scale_fill_brewer(palette="Set1")+
  facet_wrap(~age_cohort)+
  theme(legend.position="none")+
  ylab("Proportion Looking to Exit\n(Anticipatory Window, First Trial)")
overall_p_sufficient_fam_prop_looking
ggsave(here(plot_path,"overall_proportion_first_trial_target_exit_looking_sufficient_fam_prop_looking.png"),bg="white",width=9,height=6)
```

#### Summary Statistics

```{r}
summarize_test_aoi_sufficient_fam_prop_looking <- summarize_participant_test_first_trial %>%
  filter(fam_prop_exit>0.5) %>%
  group_by(age_cohort,condition) %>%
  summarize(
    participant_num=sum(!is.na(prop_exit)),
    mean_target_looking=mean(prop_exit,na.rm=T),
    sd_target_looking=sd(prop_exit,na.rm=T),
    mean_target_looking_general = mean(prop_general, na.rm=T),
    sd_target_looking_general=sd(prop_general,na.rm=T),
  )

summarize_test_aoi_sufficient_fam_prop_looking %>%
  knitr::kable()
```
#### Main Model

Fitting the main Bayesian hierarchical model testing the effect of condition (ignorance vs. knowledge) on first-trial proportion target looking during the anticipatory window for only those participants who fixated the target more than half of the time during all familiarization trial.

##### Toddlers

```{r}
#set the prior
priors <-c(
  set_prior("uniform(0, 1)", lb=0,ub=1,class = "Intercept"), #uniform distribution for intercept
  set_prior("normal(0, .1)", class = "b"), # normal distribution for fixed-effect coefficients
  set_prior("normal(0, .05)", class = "sd"), #normal distribution for sd/ random effects
  set_prior("lkj(2)", class = "L")) # lkj distribution for covariance matrix/Cholesky Factor?

bm_aoi_toddlers_sufficient_fam_prop_looking <- brm(prop_exit ~ 1+condition_c*age_mo_c+(1+condition_c*age_mo_c|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_first_trial, age_cohort=="toddlers" & fam_prop_exit>0.5),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_toddlers_sufficient_fam_prop_looking)

saveRDS(bm_aoi_toddlers_sufficient_fam_prop_looking, file = here(RESULTS_FOLDER,"bm_aoi_toddlers_sufficient_fam_prop_looking.rds"))
```

Summarize outcomes

```{r}
#get_variables(bm_aoi_toddlers)
#get main coefficient estimate and HDI
bm_aoi_toddlers_sufficient_fam_prop_looking %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_sufficient_fam_prop_looking %>%
  spread_draws(b_age_mo_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_sufficient_fam_prop_looking %>%
  spread_draws(`b_condition_c:age_mo_c`, sigma) %>%
  mean_hdi(.width = 0.95)
```

Visualize model coefficients

```{r}
bm_aoi_toddlers_sufficient_fam_prop_looking %>%
  spread_draws(b_condition_c,b_age_mo_c,`b_condition_c:age_mo_c`, sigma) %>%
  pivot_longer(cols = starts_with("b_"), names_to = "coefficient", values_to = "b") %>%
  ggplot(aes(x = coefficient,y=b)) +
  stat_halfeye()+
  geom_hline(yintercept=0,linetype="dashed")+
  theme_cowplot()+
  scale_x_discrete(limits=c("b_condition_c:age_mo_c","b_age_mo_c","b_condition_c"),labels=c("Condition x Age","Age","Condition"))+
  ylab("Model Coefficient Estimate")+
  xlab("Model Predictor")+
  coord_flip()
ggsave(here(plot_path,"test_toddlers_model_coefficients_sufficient_fam_prop_looking.png"),bg="white",width=9,height=6)
```


Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_toddlers_sufficient_fam_prop_looking <- hypothesis(bm_aoi_toddlers_sufficient_fam_prop_looking, "condition_c = 0", class="b")
h_aoi_toddlers_sufficient_fam_prop_looking
plot(h_aoi_toddlers_sufficient_fam_prop_looking)
# evidence in favor of condition being different from zero
1/h_aoi_toddlers_sufficient_fam_prop_looking$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_toddlers_sufficient_fam_prop_looking <-  update(bm_aoi_toddlers_sufficient_fam_prop_looking, formula = ~ .-condition_c)
summary(null_aoi_toddlers_sufficient_fam_prop_looking)
brms::bayes_factor(bm_aoi_toddlers_sufficient_fam_prop_looking, null_aoi_toddlers_sufficient_fam_prop_looking)
```

##### Adults

```{r}
bm_aoi_adults_sufficient_fam_prop_looking <- brm(prop_exit ~ 1+condition_c+(1+condition_c|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_first_trial,age_cohort=="adults"&fam_prop_exit>=0.5),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_adults_sufficient_fam_prop_looking)

saveRDS(bm_aoi_adults_sufficient_fam_prop_looking, file = here(RESULTS_FOLDER,"bm_aoi_adults_sufficient_fam_prop_looking.rds"))
```

```{r}
#get main coefficient estimate and HDI
bm_aoi_adults_sufficient_fam_prop_looking %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)
```

Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_adults_sufficient_fam_prop_looking <- hypothesis(bm_aoi_adults_sufficient_fam_prop_looking, "condition_c = 0", class="b")
h_aoi_adults_sufficient_fam_prop_looking
plot(h_aoi_adults_sufficient_fam_prop_looking)
# evidence in favor of condition being different from zero
1/h_aoi_adults_sufficient_fam_prop_looking$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_adults_sufficient_fam_prop_looking <-  update(bm_aoi_adults_sufficient_fam_prop_looking, formula = ~ .-condition_c)
summary(null_aoi_adults_sufficient_fam_prop_looking)
brms::bayes_factor(bm_aoi_adults_sufficient_fam_prop_looking, null_aoi_adults_sufficient_fam_prop_looking)
```

### 2.c. Correlation between familiarization and test

#### Plot 

```{r}
correlation_plot_fam_test <- ggplot(summarize_participant_test_first_trial,aes(fam_prop_exit,prop_exit,color=condition))+
  geom_hline(yintercept=0.5,linetype="dashed")+
  geom_point(alpha=0.25)+
  geom_smooth(method="lm")+
  facet_wrap(~age_cohort)+
  theme_cowplot()+
  scale_color_brewer(palette="Set1")+
  scale_fill_brewer(palette="Set1")+
  xlab("Overall Proportion Target Looking during Familiarization")+
  ylab("Proportion Looking to Exit\n(Anticipatory Window, First Trial)")
correlation_plot_fam_test
ggsave(here(plot_path,"correlation_plot_fam_test.png"),bg="white",width=9,height=6)

#correlation function
compute_correlation <- function(data){
  result <- cor.test(data$fam_prop_exit,data$prop_exit)
  #return the estimate, p-value,df, and test statistic of cor.test
  
  return(data.frame(
    correlation_estimate=result$estimate,
    correlation_df = result$parameter,
    correlation_p_value=result$p.value,
    correlation_statistic=result$statistic))
}
#correlation between familiarization and test
correlation_fam_test_overall <- summarize_participant_test_first_trial %>%
  select(age_cohort,fam_prop_exit,prop_exit) %>%
  group_by(age_cohort) %>%
  nest() %>%
  #use map to compute correlation
  summarize(correlation=map(data,compute_correlation)) %>%
  #extract the correlation values into tidy data frame
  unnest(correlation)

correlation_fam_test_overall %>%
  knitr::kable()

correlation_fam_test_by_age <- summarize_participant_test_first_trial %>%
  select(age_cohort,condition,fam_prop_exit,prop_exit) %>%
  group_by(age_cohort,condition) %>%
  nest() %>%
  #use map to compute correlation
  summarize(correlation=map(data,compute_correlation)) %>%
  #extract the correlation values into tidy data frame
  unnest(correlation)

correlation_fam_test_by_age %>%
  knitr::kable()

```


## 3. If we have a sufficiently large sample of participants tested with online sources (e.g., contributions of at least 32 participants), we will conduct a separate analysis with a model term for online participants that estimates whether condition effects are different in this population. We will further report whether exclusion rates are different for this population.

### Data collection type: in-lab vs. web-based

#### Summary Statistics

```{r}
summarize_test_aoi_method <- summarize_participant_test_first_trial %>%
  group_by(age_cohort,lab_id,participant_lab_id,participant_id,condition,condition_c,data_type,method_c) %>%
  summarize(
    n=n(),
    mean_subj_prop_exit=mean(prop_exit,na.rm=T)
  ) %>%
  group_by(age_cohort,condition,condition_c, data_type, method_c) %>%
  summarize(
    participant_num=sum(!is.na(mean_subj_prop_exit)),
    mean_target_looking=mean(mean_subj_prop_exit,na.rm=T),
    sd_target_looking=sd(mean_subj_prop_exit,na.rm=T),
     t_test = list(broom::tidy(t.test(mean_subj_prop_exit, alternative = "two.sided", mu=0.5)))) %>%
  mutate(
    #95% CIs
    lower_ci_target_looking = mean_target_looking - qt(1 - (0.05 / 2), participant_num - 1) * sd_target_looking/sqrt(participant_num),
    upper_ci_target_looking = mean_target_looking + qt(1 - (0.05 / 2), participant_num - 1) * sd_target_looking/sqrt(participant_num),
    #mean_target_looking_general = mean(prop_general, na.rm=T),
   # sd_target_looking_general=sd(prop_general,na.rm=T),
    lower_ci_target_looking_general = mean_target_looking - qt(1 - (0.05 / 2), participant_num - 1) * sd_target_looking/sqrt(participant_num),
    upper_ci_target_looking_general = mean_target_looking + qt(1 - (0.05 / 2), participant_num - 1) * sd_target_looking/sqrt(participant_num),
    p.value = purrr::map(t_test, ~select(.x, c('p.value', 'parameter','statistic')))
  ) %>%
  select(-t_test) %>%
  unnest(p.value) %>%
  rename(
    tval=statistic,
    df=parameter
  )
  

summarize_test_aoi_method %>%
  knitr::kable()
```

### Main Model

Fitting the main Bayesian hierarchical model testing the effect of condition (ignorance vs. knowledge) and method (in-lab vs. web-based) on first-trial proportion target looking during the anticipatory window.

#### Toddlers

```{r}
#set the prior
priors <-c(
  set_prior("uniform(0, 1)", lb=0,ub=1,class = "Intercept"), #uniform distribution for intercept
  set_prior("normal(0, .1)", class = "b"), # normal distribution for fixed-effect coefficients
  set_prior("normal(0, .05)", class = "sd"), #normal distribution for sd/ random effects
  set_prior("lkj(2)", class = "L")) # lkj distribution for covariance matrix/Cholesky Factor?

bm_aoi_toddlers_method <- brm(prop_exit ~ 1+condition_c*method_c+(1+condition_c*method_c|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_first_trial,age_cohort=="toddlers"),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_toddlers_method)
prior_summary(bm_aoi_toddlers_method)

saveRDS(bm_aoi_toddlers_method, file = here(RESULTS_FOLDER,"bm_aoi_toddlers_method.rds"))
```

Summarize outcomes

```{r}
#get_variables(bm_aoi_toddlers)
#get main coefficient estimate and HDI
bm_aoi_toddlers_method %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_method %>%
  spread_draws(b_method_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_toddlers_method %>%
  spread_draws(`b_condition_c:method_c`, sigma) %>%
  mean_hdi(.width = 0.95)
```

Visualize model coefficients

```{r}
bm_aoi_toddlers_method %>%
  spread_draws(b_condition_c,b_method_c,`b_condition_c:method_c`, sigma) %>%
  pivot_longer(cols = starts_with("b_"), names_to = "coefficient", values_to = "b") %>%
  ggplot(aes(x = coefficient,y=b)) +
  stat_halfeye()+
  geom_hline(yintercept=0,linetype="dashed")+
  theme_cowplot()+
  scale_x_discrete(limits=c("b_condition_c:method_c","b_method_c","b_condition_c"),labels=c("Condition x Method","Method","Condition"))+
  ylab("Model Coefficient Estimate")+
  xlab("Model Predictor")+
  coord_flip()
ggsave(here(plot_path,"test_toddlers_model_coefficients_method.png"),bg="white",width=9,height=6)
```


Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_toddlers_method <- hypothesis(bm_aoi_toddlers_method, "method_c = 0", class="b")
h_aoi_toddlers_method
plot(h_aoi_toddlers_method)
# evidence in favor of condition being different from zero
1/h_aoi_toddlers_method$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_toddlers_method <-  update(bm_aoi_toddlers_method, formula = ~ .-method_c)
summary(null_aoi_toddlers_method)
brms::bayes_factor(bm_aoi_toddlers_method, null_aoi_toddlers_method)
```


#### Adults

```{r}
bm_aoi_adults_method <- brm(prop_exit ~ 1+condition_c*method_c+(1+condition_c*method_c|lab_id),
         family=gaussian,
         prior = priors,
         save_pars = save_pars(all = TRUE),
        filter(summarize_participant_test_first_trial,age_cohort=="adults"),
        warmup = 1000, 
        iter = 2000, 
        chains = 4, 
        cores = 4,
        seed = 123,
        sample_prior=TRUE)
summary(bm_aoi_adults_method)

saveRDS(bm_aoi_adults_method, file = here(RESULTS_FOLDER,"bm_aoi_adults_method.rds"))
```
Summarize outcomes

```{r}
#get main coefficient estimate and HDI
bm_aoi_adults_method %>%
  spread_draws(b_condition_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_adults_method %>%
  spread_draws(b_method_c, sigma) %>%
  mean_hdi(.width = 0.95)

bm_aoi_adults_method %>%
  spread_draws(`b_condition_c:method_c`, sigma) %>%
  mean_hdi(.width = 0.95)
```

Visualize model coefficients

```{r}
bm_aoi_adults_method %>%
  spread_draws(b_condition_c,b_method_c,`b_condition_c:method_c`, sigma) %>%
  pivot_longer(cols = starts_with("b_"), names_to = "coefficient", values_to = "b") %>%
  ggplot(aes(x = coefficient,y=b)) +
  stat_halfeye()+
  geom_hline(yintercept=0,linetype="dashed")+
  theme_cowplot()+
  scale_x_discrete(limits=c("b_condition_c:b_method_c","b_method_c","b_condition_c"),labels=c("Condition x Method","Method","Condition"))+
  ylab("Model Coefficient Estimate")+
  xlab("Model Predictor")+
  coord_flip()
ggsave(here(plot_path,"test_adults_model_coefficients_method.png"),bg="white",width=9,height=6)
```

Hypothesis test/ compute Bayes Factor

```{r}
h_aoi_adults_method <- hypothesis(bm_aoi_adults_method, "method_c = 0")
h_aoi_adults_method 
plot(h_aoi_adults_method)
# evidence in favor of condition being different from zero
1/h_aoi_adults_method$hypothesis$Evid.Ratio
```

Alternate Bayes factor approach

```{r}
null_aoi_adults_method <-  update(bm_aoi_adults_method, formula = ~ .-method_c)
summary(null_aoi_adults_method)
brms::bayes_factor(bm_aoi_adults_method, null_aoi_adults_method)
```


## 4. If we observe substantial looking (defined *post hoc* by evaluating scatter plot videos of gaze data) to the boxes as well as the tunnel exit AOIs, we will conduct an exploratory analysis using tighter AOIs around tunnel exits and boxes, asking whether box and tunnel looking vary separately by age or by condition. In particular, we expect that the difference in AL between the two conditions will be bigger for the tunnel exits than for the box (as looks to the correct box might indicate looks to the target, which is in the same box for both conditions, rather than action anticipation).

## 5. Looking patterns during mouse's change of location

Introduce new AOIs during location change: bear and mouse
Rough dimensions of new AOIs (include all movements during TOI + double-check using the heatmap-videos):

Time frame of interest (TOI; from “Box A reopens and mouse jumps out” to “Box B closes with mouse inside”)
IG: 20:52 - 25:46
KNOW: 24:63 - 29:00


### 5.1. Compare looking patterns of toddlers and adults

Hypothesis 1: adults shift more than toddlers

Create a variable shifts_num that counts the number of times the participants shift their gaze between bear and mouse. Also compute the times participants fixate the mouse or the bear during location change.

ignorance t>=20520 & t<=25460
knowledge t>=24630 & t<=29000


```{r}

 # Function to compute shifts and fixation times during location change (specified time intervals for each condition)
compute_shifts_and_fixation_times <- function(data, condition) {
  # Define time intervals for each condition
  location_changes <- list(
    ignorance = c(20520, 25460),
    knowledge = c(24630, 29000)
  )
  
  # Get the time interval for the specified condition
  location_change <- location_changes[[condition]]
  
  # Filter the data based on the time interval
  filtered_data <- data %>%
    filter(t >= location_change[1] & t <= location_change[2]) %>%
    filter(aoi_bearmouse_special %in% c("bear", "mouse")) %>%
    arrange(participant_lab_id, t)
  
  # Calculate number of shifts and fixation times on mouse and bear during location change of mouse
  results <- filtered_data %>%
    group_by(participant_lab_id) %>%
    mutate(
      shift = (aoi_bearmouse_special != lag(aoi_bearmouse_special)) & !is.na(lag(aoi_bearmouse_special)),
      fixation_time = lead(t, default = last(t)) - t
    ) %>%
    summarise(
      num_shifts = sum(shift, na.rm = TRUE),
      total_fixation_bear = sum(fixation_time[aoi_bearmouse_special == "bear"], na.rm = TRUE),
      total_fixation_mouse = sum(fixation_time[aoi_bearmouse_special == "mouse"], na.rm = TRUE)
    ) %>%
    ungroup()
  
  return(results)
}

# Apply the function to the dataset for both conditions
location_change_ignorance <- compute_shifts_and_fixation_times(test_data, "ignorance")
location_change_knowledge <- compute_shifts_and_fixation_times(test_data, "knowledge")
```

### 5.1. Infants gaze shifts during location change as a function of AL
Hypothesis 2:  “Bear-trackers” have stronger looking bias in KNOW

MSS What is a bear-tracker? Is that a participant whose fixation times for the bear are longer than for the mouse?

Hypothesis 3: “High-Shifters” (during A to B transfer) have stronger looking bias in KNOW

MSS Could this possibly be a correlation or a model that includes shift_num as fixed effect?

Hypothesis 4:  More looking at the bear in KNOW vs. IG → speaks in favor of distraction; similarly, more looking at the mouse during change in ign compared to know cond

