---
title: "MB2 Pupillometry Analysis"
format: html
---


```{r}
library(tidyverse)
library(here)
library(glue)
library(assertthat)

source(here('helper','ensure_repo_structure.R'))
plot_path <- here("plots")

load(here(INTERMEDIATE_FOLDER, INTERMEDIATE_006))
```

Basic cleaning:
1. Create `pupil_size` column which should be the mean of `pupil_left` and `pupil_right`.
2. For cases in which `x` and `y` are NA, `pupil_size` should be NA, not 0.
```{r}
data_pupillometry <- data_preprocessed_post_exclusions |> 
  mutate(pupil_size = rowMeans(bind_cols(pupil_left, pupil_right), na.rm = TRUE),
         pupil_size = ifelse(is.na(x) & is.na(y), NA, pupil_size))
```

Sanity check.
Some EyeLink labs have long right tails; Nijmegen also has some density in the very low sizes that might be artefactual.
```{r}
data_pupillometry |> 
  filter(age_cohort == "adults") |> 
  ggplot() +
  geom_density(aes(x = pupil_size, col = lab_id)) +
  theme_classic() +
  theme(legend.position = "none") +
  facet_wrap(~ lab_id, scales = "free")
```

```{r}
data_pupillometry |> 
  filter(age_cohort == "toddlers") |> 
  ggplot() +
  geom_density(aes(x = pupil_size, col = lab_id)) +
  theme_classic() +
  theme(legend.position = "none") +
  facet_wrap(~ lab_id, scales = "free")
```

Might need to consider deblinking and detransienting to remove artifacts (a lot of the low-value responses are surrounding NA instances); perhaps with a window of 25ms or 50ms.

Examining for second test trial---all included participants also have a valid second test trial :)
```{r}
summarized_valid_second_test_trials <- data_pupillometry |> 
  filter(condition %in% c("ignorance","knowledge"),
         trial_num == 6) |> 
  mutate(
    valid_second_test_trial = case_when(
      trial_error == "no" ~ 1,
      trial_error == "yes" ~ 0,
      TRUE ~ NA
    )
  ) |> 
  select(lab_id, participant_lab_id, participant_id, 
         age_cohort, valid_second_test_trial) |> 
  distinct()

data_pupillometry <- data_pupillometry |> 
  left_join(summarized_valid_second_test_trials,
            by = join_by(participant_lab_id, participant_id, 
                         lab_id, age_cohort)) |> 
  mutate(valid_second_test_trial = ifelse(is.na(valid_second_test_trial), 
                                          0, valid_second_test_trial))

# validate
assert_that(sum(is.na(data_pupillometry$valid_second_test_trial)) == 0)
```

Merge in eyetracker info
```{r}
dataset_sheet <- read_csv(here("metadata", "dataset_sheet.csv"))

data_pupillometry <- data_pupillometry |> 
  mutate(data_id = glue("{lab_id}_{age_cohort}")) |> 
  left_join(dataset_sheet |> select(data_id, tracker_type),
            by = join_by(data_id)) |> 
  select(-data_id) |> 
  mutate(tracker_type = str_remove(tracker_type, " .*"))
```

