---
title: "MB2 Pupillometry Analysis"
format: html
---


```{r}
library(tidyverse)
library(here)
library(glue)
library(assertthat)

source(here('helper','ensure_repo_structure.R'))
plot_path <- here("plots")

load(here(INTERMEDIATE_FOLDER, INTERMEDIATE_006))
```

Basic cleaning:
1. Remove all web-based data.
2. Create `pupil_size` column which should be the mean of `pupil_left` and `pupil_right`.
3. For cases in which `x` and `y` are NA, `pupil_size` should be NA, not 0.
```{r}
data_pupillometry <- data_preprocessed_post_exclusions |> 
  filter(data_type=="in-lab") |> 
  mutate(pupil_left = ifelse(is.na(x) & is.na(y), NA, # If both x and y are NA, pupil_left should be NA, not 0
                          ifelse(is.na(pupil_left), pupil_right, pupil_left)), # If pupil_left is NA, take value of pupil_right
         pupil_right = ifelse(is.na(x) & is.na(y), NA, # If both x and y are NA, pupil_right should be NA, not 0
                          ifelse(is.na(pupil_right), pupil_left, pupil_right))) # If pupil_right is NA, take value of pupil_left
                  
```

Sanity check.
Some EyeLink labs have long right tails; Nijmegen also has some density in the very low sizes that might be artefactual.
```{r}
data_pupillometry |> 
  filter(age_cohort == "adults") |> 
  ggplot() +
  geom_density(aes(x = pupil_left, col = lab_id)) +
  theme_classic() +
  theme(legend.position = "none") +
  facet_wrap(~ lab_id, scales = "free")

data_pupillometry |> 
  filter(age_cohort == "adults") |> 
  ggplot() +
  geom_density(aes(x = pupil_right, col = lab_id)) +
  theme_classic() +
  theme(legend.position = "none") +
  facet_wrap(~ lab_id, scales = "free")
```

```{r}
data_pupillometry |> 
  filter(age_cohort == "toddlers") |> 
  ggplot() +
  geom_density(aes(x = pupil_left, col = lab_id)) +
  theme_classic() +
  theme(legend.position = "none") +
  facet_wrap(~ lab_id, scales = "free")

data_pupillometry |> 
  filter(age_cohort == "toddlers") |> 
  ggplot() +
  geom_density(aes(x = pupil_right, col = lab_id)) +
  theme_classic() +
  theme(legend.position = "none") +
  facet_wrap(~ lab_id, scales = "free")
```

Might need to consider deblinking and detransienting to remove artifacts (a lot of the low-value responses are surrounding NA instances); perhaps with a window of 25ms or 50ms.

Examining for second test trial---all included participants also have a valid second test trial :)
```{r}
summarized_valid_second_test_trials <- data_pupillometry |> 
  filter(condition %in% c("ignorance","knowledge"),
         trial_num == 6) |> 
  mutate(
    valid_second_test_trial = case_when(
      trial_error == "no" ~ 1,
      trial_error == "yes" ~ 0,
      TRUE ~ NA
    )
  ) |> 
  select(lab_id, participant_lab_id, participant_id, 
         age_cohort, valid_second_test_trial) |> 
  distinct()

data_pupillometry <- data_pupillometry |> 
  left_join(summarized_valid_second_test_trials,
            by = join_by(participant_lab_id, participant_id, 
                         lab_id, age_cohort)) |> 
  mutate(valid_second_test_trial = ifelse(is.na(valid_second_test_trial), 
                                          0, valid_second_test_trial))

# validate
assert_that(sum(is.na(data_pupillometry$valid_second_test_trial)) == 0)
```

Merge in eyetracker info + Create new variable that contains eyetracker info: Eyelink, Tobii, or SMI
```{r}
dataset_sheet <- read_csv(here("metadata", "dataset_sheet.csv"))
data_pupillometry <- data_pupillometry |> 
  mutate(data_id = glue("{lab_id}_{age_cohort}")) |> 
  left_join(dataset_sheet |> select(data_id, tracker_type),
            by = join_by(data_id)) |> 
  select(-data_id)
  # The above creates two columns, tracker_type.x & tracker_type.y
  # Check that they are identical:
  identical(data_pupillometry[['tracker_type.y']],data_pupillometry[['tracker_type.x']])
  # Then use one of them:
  data_pupillometry <- data_pupillometry |>
  mutate(eyetracker_type = str_remove(tracker_type.y, " .*"))
```

Create new variable that contains outcome info: congruent, incongruent
```{r}
data_pupillometry$outcome <- ifelse(grepl("_CON$", data_pupillometry$media_name), "congruent",
                     ifelse(grepl("_INC$", data_pupillometry$media_name), "incongruent", NA))
```

Saving pupillometry dataset to use for multiverse
```{r}
save(data_pupillometry, file = here(INTERMEDIATE_FOLDER, INTERMEDIATE_008))
```

Creating heatmaps for 5s-window after the point of disambiguation
```{r}
library(png)
img.r <- as.raster(readPNG(here('helper', 'stim.png')),interpolate=F)

MB2P_DIR <- here('MB2P')
CHECKING_DIR <- here(MB2P_DIR, 'manual_data_checking_pupil')
CHECKING_HEATMAP_DIR <- here(CHECKING_DIR, 'heatmaps_for_pupil')

data_pupillometry %>% 
  filter((trial_num %in% c('6'))) %>% 
  filter(t_norm>=0 & t_norm<=5000)  %>%
  group_by(lab_id, media_name) %>%
  group_walk(function(data, grouping){
    print(grouping$lab_id)
    
    #if(!(grouping$lab_id %in% labs_to_check)){
    #  return(NA)
    #}
    
    labdir = here(CHECKING_HEATMAP_DIR, grouping$lab_id)
    dir.create(labdir, showWarnings = FALSE)
    tryCatch(
    ggsave(
      here(labdir, paste0(grouping$media_name, '__', grouping$lab_id, '.png')),
      plot = 
        ggplot(data, aes(x,y)) + 
          annotation_raster(img.r, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf)+
          stat_density2d(geom = "polygon", aes(fill=..level.., alpha = ..level..), size= 20, bins= 500) + 
          scale_fill_gradient(low="blue",high="red") +
          scale_alpha_continuous(range=c(0.01,1.0), guide = FALSE) +
          scale_x_continuous(limits=c(0,dim(img.r)[2]),expand=c(0,0))+
          scale_y_continuous(limits=c(0,dim(img.r)[1]),expand=c(0,0))+
          coord_fixed(),
      width = 7,
      height = 5,
      units = "in"
      ), error = function(e) print(e))
  })
```