---
title: "Data Integrity"
author: "The ManyBabies Analysis Team"
date: '`r format(Sys.time(), "%a %b %d %X %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
editor_options: 
  chunk_output_type: inline
---
```{r libraries}
source(here::here("helper/common.R"))
```

# File reading - xy data only

```{r}
labs <- dir(here::here("pilot_data"))

xy <- labs %>%
  map_df(function(lab){
    xy_data <- read_csv(here(paste0("pilot_data/",
                                    lab, "/processed_data/xy_data.csv")))
    datasets <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/datasets.csv")))
    trials <- read_csv(here(paste0("pilot_data/",
                                   lab,"/processed_data/trials.csv"))) 
    subjects <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/subjects.csv"))) 
    left_join(xy_data, subjects) %>%
      left_join(datasets) %>%
      left_join(trials) %>%
      select(lab_subject_id, monitor_size_x, monitor_size_y, x, y, t, 
             tracker, error, lab_dataset_id, trial_id, lab_trial_id) %>%
      rename(subid = lab_subject_id, 
             lab = lab_dataset_id, 
             stimulus = lab_trial_id)
    
  })
```

```{r filters}
# filter subjects marked error
xy <- filter(xy, error == F)

# print trials under 35s
group_by(xy, lab, trial_id, subid) %>%
  summarise(time_range = (max(t) - min(t))/1000)  %>%
  filter(time_range <= 35) %>%
  kable(digits=2)

# filter trials under 35s (which are not complete trials)
xy <- group_by(xy, lab, trial_id, subid) %>%
  mutate(time_range = (max(t) - min(t))/1000) %>%
  filter(time_range > 35)
# print trial time ranges by lab
ungroup(xy) %>%
  group_by(lab) %>% 
  summarise(shortest_trial=min(time_range),
            longest_trial=max(time_range)) %>%
  kable(digits=2)

# print subjects who did not complete all trials and then filter
xy %>%
  group_by(lab, subid) %>%
  summarise(trials_completed = length(unique(trial_id))) %>%
  filter(trials_completed < 8) %>%
  kable(digits=2)

xy <- ungroup(xy) %>%
  group_by(lab, subid) %>%
  filter(length(unique(trial_id)) >= 8)
```

# Raw data checks

Visual inspection of gaze distribution on the screen to see if there is systematic offset and/or extreme values.

```{r add a column to correct for stimuli size differences}
# transform for plotting, assuming the origin is upper left
# and video is centered within monitor
xy <- mutate(xy,
             video_size_x = ifelse(grepl("1200", stimulus), 1200, 1280),
             video_size_y = ifelse(grepl("900", stimulus), 900, 960),
             x_plot = x - (monitor_size_x - video_size_x)/2,
             y_plot = (monitor_size_y - y) - (monitor_size_y - video_size_y)/2)
```


## SMI data

```{r SMI check}
smi <- filter(xy, tracker == "smi")
```

### SMI histogram to check for extreme values

```{r histograms of coordinate distribution}
hist(smi$x)
hist(smi$y)
```

### SMI gaze distribution

```{r SMI gaze map}
ggplot(sample_n(smi, 5000),
       aes(x = x_plot, y = y_plot, col = lab)) +
  geom_point() + 
  labs(x = "x", y = "y", col = "Lab") +
  ggtitle("SMI gaze map, unfixed axis")

ggplot(sample_n(smi, 5000),
       aes(x = x_plot, y = y_plot, col = lab)) +
  geom_point() + 
  xlim(0, 1200) +
  ylim(0, 900) +
  labs(x = "x", y = "y", col = "Lab") +
  ggtitle("SMI gaze map, fixed axis")
  
```

### SMI heat map

```{r SMI heat map}
ggplot(smi, 
       aes(x = x_plot, y = y_plot)) +
  stat_density2d(aes(fill = ..density..), geom = 'tile', contour = F) + 
  xlim(0,1200) +
  ylim(0,900) +
  scale_fill_distiller(palette = "RdYlBu") +
  ggtitle("SMI gaze heat map")
```

## Tobii data

```{r Tobii check}
tobii <- filter(xy, tracker == "tobii")
```

### Tobii histogram to check for extreme values

```{r historgrams for coordinates}
hist(tobii$x)
hist(tobii$y)
```

### Tobii gaze distribution

```{r Tobii gaze maps}
ggplot(sample_n(tobii, 5000),
       aes(x = x_plot, y = y_plot, col = lab)) +
  geom_point() + 
  labs(x = "x", y = "y", col = "Lab") +
  ggtitle("Tobii gaze map")

ggplot(sample_n(tobii, 5000),
       aes(x = x_plot, y = y_plot, col = lab)) +
  geom_point(alpha = .1) +
  xlim(0, 1200) +
  ylim(0, 900) +
  labs(x = "x", y = "y", col = "Lab") +
  ggtitle("Tobii gaze map, fixed axis")
```



### Tobii heat map

```{r Tobii heat mmap}
ggplot(tobii, 
       aes(x = x_plot, y = y_plot)) +
  xlim(0,1200) +
  ylim(0,900) +
  stat_density2d(aes(fill = ..density..), geom = 'tile', contour = F) + 
  scale_fill_distiller(palette = "RdYlBu") +
  ggtitle("Tobii gaze heat map")
```

## Eyelink data

```{r eyelink data}
eyelink <- filter(xy, tracker == "eyelink")
```

### Eyelink Histogram

```{r}
hist(eyelink$x)
hist(eyelink$y)
```

### Eyelink gaze distribution

```{r eyelink gaze maps}
ggplot(sample_n(eyelink, 1000),
       aes(x = x_plot, y = y_plot, col = lab)) +
  geom_point() +
  labs(x = "x", y = "y", col = "Lab") +
  ggtitle("Eyelink gaze map, unfixed axis")

ggplot(sample_n(eyelink, 1000),
       aes(x = x_plot, y = y_plot, col = lab)) +
  geom_point(alpha = 0.05) +
  xlim(0, 1200) +
  ylim(0, 900) +
  labs(x = "x", y = "y", col = "Lab") +
  ggtitle("Eyelink gaze map, fixed axis")
```

### Eyelink heat map

```{r eyelink density}
ggplot(sample_n(eyelink, 20000), 
       aes(x = x_plot, y = y_plot)) +
  stat_density2d(aes(fill = ..density..), geom = 'tile', contour = F) + 
  xlim(0,1200) +
  ylim(0,900) +
  scale_fill_distiller(palette = "RdYlBu") +
  ggtitle("Eyelink gaze heat map")
```



