---
title: "MB2 Pilot Analysis"
author: "The ManyBabies Analysis Team"
date: '`r format(Sys.time(), "%a %b %d %X %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
editor_options: 
  chunk_output_type: inline
---

```{r libraries}
suppressMessages(library(here))
suppressMessages(library(jpeg))
suppressMessages(library(grid))
suppressMessages(library(lmerTest))
suppressMessages(library(car))

source(here::here("helper/common.R"))
source(here("helper/preprocessing_helper.R"))
```


# Intro

Pilot data analysis for MB2.

We can re-preprocess all of our data, this is set not to evaluate by default. In order to do this, you will need to register with Eyelink to get their binary package and then install `edfR`.

```{r, eval=FALSE}
labs <- dir(here::here("pilot_data"))

for (lab in labs) {
  print(lab)
  source(here::here("pilot_data", lab, "import.R"))
}

```


# File reading


```{r}
labs <- dir(here::here("pilot_data"))

d <- labs %>%
  map_df(function(lab) {
    aoi_data <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/aoi_data.csv"))) 
    subjects <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/subjects.csv"))) 
    trials <- read_csv(here(paste0("pilot_data/",
                                   lab,"/processed_data/trials.csv"))) 
    datasets <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/datasets.csv")))
    
    left_join(aoi_data, subjects) %>%
      left_join(trials) %>%
      left_join(datasets) %>%
      select(lab_subject_id, lab_dataset_id, lab_trial_id, trial_id, 
             age, t, aoi, trial_num, error) %>%
      rename(subid = lab_subject_id, 
             lab = lab_dataset_id, 
             stimulus = lab_trial_id)
  })
```

# Exclusions

```{r}
# filter subjects marked error
d <- filter(d, error == F)

# print trials under 35s
group_by(d, lab, trial_id, subid) %>%
  summarise(time_range = (max(t) - min(t))/1000)  %>%
  filter(time_range <= 35) %>%
  kable(digits=2)

# filter trials under 35s (which are not complete trials)
d <- group_by(d, lab, trial_id, subid) %>%
  mutate(time_range = (max(t) - min(t))/1000) %>%
  filter(time_range > 35)

# print trial time ranges by lab
ungroup(d) %>%
  group_by(lab) %>% 
  summarise(shortest_trial=min(time_range),
            longest_trial=max(time_range)) %>%
  kable(digits=2)

# print subjects who did not complete all trials and then filter
d %>%
  group_by(lab, subid) %>%
  summarise(trials_completed = length(unique(trial_id))) %>%
  filter(trials_completed < 8) %>%
  kable(digits=2)

d <- ungroup(d) %>%
  group_by(lab, subid) %>%
  filter(length(unique(trial_id)) >= 8)
```


# Analysis

Descriptives

```{r}
d %>%
  group_by(lab, subid) %>%
  summarise(age = mean(age)) %>%
  summarise(n = n(), 
            age = mean(age)/30.25) %>%
  kable(digits = 2)
  

```

Anticipation plot across all trials. 

```{r}
ms <- d %>%
  group_by(t, trial_num) %>%
  summarise(target = mean(aoi == "target", na.rm=TRUE),
            distractor = mean(aoi == "distractor", na.rm=TRUE)) %>%
  gather(region, looking, target, distractor) 

ggplot(ms, aes(x = t, y = looking, col = region)) + 
  geom_line() + 
  geom_vline(xintercept = 120, col = "red", lty = 2)

```    

In the primary time period of interest

```{r}
ms <- d %>%
  group_by(t) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  geom_text(x = -4000, y = .95, group = 1, col = "black", 
            label = "Anticipation", hjust = 0) + 
  geom_text(x = 200, y = .95, group = 1, col = "black", 
            label = "Reaction", hjust = 0)
```

Now, broken down by trial.
Summary across anticipation window.

```{r}
ms <- d %>%
  filter(t > -4000, t < 120) %>%
  group_by(lab, subid, trial_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE)) %>%
  group_by(trial_num) %>%
  langcog::multi_boot_standard(col = "target", na.rm = TRUE)


ggplot(ms, aes(x = trial_num, y = mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_line()
```
  
   
Binned for cleaner curves

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, "Trials 1-4", "Trials 5-8")) %>%
  group_by(t, block) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) +
  geom_vline(xintercept = 120, col = "black", lty = 3) + 
  annotate("text", x = -3800, y = 1, col = "black",
            label = "Anticipation", hjust = 0) +
  annotate("text", x = 200, y = 1, col = "black", 
            label = "Reaction", hjust = 0) + 
  ggthemes::scale_color_solarized(name = "Area of Interest") + 
  xlab("Time (msec)") + 
  ylab("Proportion gaze in AOI") + 
  theme(legend.position = "bottom") + 
  facet_wrap(~block)
```

And by lab:

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, 1, 2)) %>%
  group_by(t, lab, block) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) +
  facet_grid(lab~block)
```

# Main analysis 1: First anticipatory look

First, create a function that extract the time stamp of first aoi
```{r}
t_first_aoi <- function(df){
  
  df <- df %>% 
    filter(t >= -4000, t <= 120, aoi == c("target", "distractor")) 
  
 df = df %>% group_by(subid, trial_num) %>% mutate(first_look_time = t[1])
  
  return(df)
}
```

Second, create a dataframe to identify the first look and see if the first look is >100ms
```{r}
df_t_first_aoi <- d %>% split(.$subid, .$trial_num) %>% 
  map_df(t_first_aoi) %>% 
  mutate(aoi_dummy = case_when(aoi == "target" ~ 1, aoi == "distractor" ~ 0),
         subid_trial = paste0(subid, trial_num)) 

df_t_first_aoi <- df_t_first_aoi %>% 
                  group_by(subid, trial_num) %>% 
                  mutate(diff = aoi_dummy - lag(aoi_dummy))

head_4 <- function(df){df %>% slice(1:4)}

df_t_4 <- df_t_first_aoi %>% split(.$subid, .$trial_num) %>%
                  map_df(head_4) %>%
                  filter(diff != 0) %>% 
                  mutate(subid_trial = paste0(subid, trial_num))

unique(df_t_4$subid_trial) 

df_t_change_kids <- df_t_first_aoi %>% 
                    mutate(subid_trial = paste0(subid, trial_num)) %>% 
                    filter(subid_trial %in% df_t_4$subid_trial) %>% 
                    select(subid_trial, subid, trial_num, t, first_look_time, aoi, aoi_dummy)

df_t_first_aoi <- df_t_first_aoi %>% 
  select(subid_trial, subid, lab, stimulus, age, trial_num, t, first_look_time, aoi, aoi_dummy) %>% 
  filter(t == first_look_time) %>% 
  mutate(first_look_location = case_when(subid_trial == "lmu_child044" ~ 1,
                                       subid_trial == "lmu_child111" ~ 0,
                                       subid_trial == "lmu_child115" ~ 0,
                                       subid_trial == "lmu_child121" ~ 1,
                                       subid_trial == "mb2_p123" ~ 1,
                                       subid_trial == "mb2_p164" ~ 1,
                                       subid_trial == "mb2_p37" ~ 0,
                                       subid_trial == "MB2_P46" ~ 0,
                                       subid_trial == "MB2_P56" ~ 0,
                                       subid_trial == "MB2-108" ~ 0,
                                       subid_trial == "MB2-117" ~ 1,
                                       subid_trial == "MB2-124" ~ 1,
                                       subid_trial == "MB2-126" ~ 1,
                                       subid_trial == "mb2p067" ~ 1,
                                       subid_trial == "mb2p103" ~ 1,
                                       subid_trial == "mb2p114" ~ NA_real_,
                                       subid_trial == "mb2p126" ~ 0,
                                       subid_trial == "mb2p127" ~ 1,
                                       TRUE ~ aoi_dummy)) %>% 
  filter(!is.na(first_look_location))
```

## Data visaulization across different test trial
```{r}
ggplot(df_t_first_aoi, aes(x = first_look_location)) + 
  geom_bar() + 
  facet_wrap(.~trial_num, ncol = 4)
```

## Descriptive stats: mean and sd of first look location in different trials. All numbers seem to be above 50%
```{r}
df_t_first_aoi %>% 
  select(trial_num, first_look_location) %>% 
  group_by(trial_num) %>% 
  summarize(number_of_kids_each_trial = n(),
            mean(first_look_location),
            sd(first_look_location))
```

## Mixed-level analysis: First look location
```{r first look analysis, results = "asis"}

first_look_logistic <- glmer(first_look_location ~ trial_num + (1|subid), data = df_t_first_aoi, family = "binomial")

summary(first_look_logistic)

mean(df_t_first_aoi$first_look_location)
```



# Main analysis 2: Differential analysis 

## Data visualization across different test trials
```{r}
ms_proportion_trials <- d %>%
  group_by(t, trial_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  mutate(proportion_to_target = target / (target + distractor)) %>% 
  filter(t >= -4000 & t <= 120+ 4000)


ggplot(ms_proportion_trials, 
       aes(x = t, y = proportion_to_target)) +
  geom_point(alpha = 0.3) + 
  geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  geom_text(x = -4000, y = .95, group = 1, col = "black", 
            label = "Anticipation", hjust = 0 ) + 
  geom_text(x = 200, y = .95, group = 1, col = "black", 
            label = "Reaction", hjust = 0 )+
  facet_wrap(.~trial_num, ncol = 4)   
```

Create data-set for the mixed-level analysis
```{r}
ms_proportion_trials <- d %>%
  filter (t >= -4000 & t <= 120) %>% 
  group_by(trial_num, subid, lab) %>%
  summarise(mean_target = mean(aoi == "target", na.rm = TRUE),
            sem_target = sd(aoi == "target", na.rm = TRUE) / sqrt(length(!is.na(aoi))),
            mean_distractor = mean(aoi == "distractor", na.rm = TRUE), 
            sem_distractor = sd(aoi == "distractor", na.rm = TRUE) / sqrt(length(!is.na(aoi))),
            up_ci_target = mean_target + (sem_target * 1.96),
            low_ci_target = mean_target - (sem_target * 1.96),
            up_ci_distractor = mean_distractor + (sem_distractor * 1.96),
            low_ci_distractor = mean_distractor - (sem_distractor * 1.96)) %>% 
  mutate(proportion_to_target = mean_target / (mean_target + mean_distractor))
```

## Mixed-level analysis for diff-score analysis
```{r mixed-level analysis}
# Lmer_originally, I tried the following but it didn't converge:  lmer(proportion_to_target ~ trial_num + + (1|lab) + (trial_num|subid), data = ms_proportion_trials), so I changed the model to a simpler one below
prop_model <- lmer(proportion_to_target ~ trial_num + (1|subid), data = ms_proportion_trials)
summary(prop_model) #note that technically we had 68 participants, but this analysis was based on 63 kids because not all kids looked at either target/distractor between -4000 ms to 120 ms (i.e., they either looked away (missing data) or looked at other parts of the screen (other))


# did a linear hypothesis test to see if the intercept of the prop_model is signficantly higher than chance level (0.5)
linearHypothesis(prop_model, "(Intercept) = 0.5")

# the linear hypothesis test is also confirmed by calculating the z score of this intercept, I used the coefficient and the sd of the random intercept
z_intercept <- 0.7525/0.066 #much higher than 1.96,
```



<!-- # XY visualizations -->

<!-- First get data.  -->

<!-- ```{r} -->
<!-- xyd <- labs %>% -->
<!--   map_df(function(lab) { -->
<!--     xy_data <- read_csv(here(paste0("pilot_data/", -->
<!--                                      lab,"/processed_data/xy_data.csv")))  -->
<!--     subjects <- read_csv(here(paste0("pilot_data/", -->
<!--                                      lab,"/processed_data/subjects.csv")))  -->
<!--     trials <- read_csv(here(paste0("pilot_data/", -->
<!--                                    lab,"/processed_data/trials.csv")))  -->
<!--     datasets <- read_csv(here(paste0("pilot_data/", -->
<!--                                      lab,"/processed_data/datasets.csv"))) -->

<!--     left_join(xy_data, subjects) %>% -->
<!--       left_join(trials) %>% -->
<!--       left_join(datasets) %>% -->
<!--       select(lab_subject_id, lab_dataset_id, lab_trial_id, trial_id,  -->
<!--              age, t, x, y, trial_num, error) %>% -->
<!--       rename(subid = lab_subject_id,  -->
<!--              lab = lab_dataset_id,  -->
<!--              stimulus = lab_trial_id) -->
<!--   }) -->
<!-- ``` -->

<!-- Deal with timing in xy_data. TODO: do this re-zeroing by trial in the importing. -->

<!-- ```{r} -->
<!-- pod <- 30600 -->
<!-- xyd <- xyd %>% -->
<!--   group_by(subid, lab, trial_id) %>% -->
<!--   mutate(t = t - t[1], -->
<!--          t = t - pod) -->
<!-- ``` -->

<!-- TODO: add exclusions. -->

<!-- Used the `av` package to split video to 40fps images (just for resampling convenience.  -->


<!-- ```{r} -->
<!-- #FAM_LL_1200x900 -->
<!-- # https://stackoverflow.com/questions/42333085/how-to-fit-the-plot-over-a-background-image-in-r-and-ggplot2 -->
<!-- # start time: 27 seconds -->

<!-- screen_size <- c(1920,1080) -->
<!-- clip_size <- c(1200,900) -->

<!-- frame2time <- function (f) {  -->
<!--   ((f / 40)*1000) - pod -->
<!-- } -->

<!-- frames <- 1200:1205 -->
<!-- p <- list() -->

<!-- for (i in 1:length(frames)) { -->

<!--   frame <- frames[i] -->
<!--   time <- frame2time(frame) -->

<!--   img <- readJPEG(paste0("media/FAM_LL_1200x900/image_",  -->
<!--                          sprintf("%06.0f", frame),".jpg")) -->

<!--   g <- rasterGrob(img,  -->
<!--                   width = unit(1,"npc"),  -->
<!--                   height = unit(1, "npc"),  -->
<!--                   interpolate = FALSE) -->

<!--   plot_data <- xyd %>% -->
<!--     filter(str_detect(stimulus, "FAM_LL_1200x900*"),  -->
<!--            t > time, t < time + 25) -->

<!--   p[i] <- ggplot(data = plot_data) + -->
<!--     annotation_custom(g,  -->
<!--                       xmin = (screen_size[1] - clip_size[1])/2,  -->
<!--                       xmax = clip_size[1] + (screen_size[1] - clip_size[1])/2,  -->
<!--                       ymin = (screen_size[2] - clip_size[2])/2,  -->
<!--                       ymax = clip_size[2] + (screen_size[2] - clip_size[2])/2) +  -->
<!--     geom_point(aes(x = x,  -->
<!--                    y = screen_size[2] - y,  -->
<!--                    col = lab),  -->
<!--                alpha = 1) + -->
<!--     xlim(0,screen_size[1]) +  -->
<!--     ylim(0,screen_size[2]) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- foo <- d %>% -->
<!--   filter(str_detect(stimulus, "FAM_LL_1200x900*"),  -->
<!--          t > -4*40, t < 0) -->

<!-- foo %>% -->
<!--   group_by(lab) %>% -->
<!--   summarise(mean = mean(aoi == "target")) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- d %>% -->
<!--   filter(str_detect(stimulus, "FAM_LL_1200x900*"),  -->
<!--          t > -4*40, t < 0) %>% -->
<!--   group_by(lab) %>% -->
<!--   summarise(target = mean(aoi == "target"),  -->
<!--             distractor = mean(aoi == "distractor"),  -->
<!--             other = mean(aoi == "other"),  -->
<!--             na = mean(is.na(aoi))) -->
<!-- ``` -->

