---
title: "MB2 Pilot Analysis"
author: "The ManyBabies Analysis Team"
date: '`r format(Sys.time(), "%a %b %d %X %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
editor_options: 
  chunk_output_type: inline
---

```{r libraries}
suppressMessages(library(here))
suppressMessages(library(jpeg))
suppressMessages(library(grid))

source(here::here("helper/common.R"))
source(here("helper/preprocessing_helper.R"))
```


# Intro

Pilot data analysis for MB2.

We can re-preprocess all of our data, this is set not to evaluate by default. In order to do this, you will need to register with Eyelink to get their binary package and then install `edfR`.

```{r, eval=FALSE}
labs <- dir(here::here("pilot_data"))

for (lab in labs) {
  print(lab)
  source(here::here("pilot_data", lab, "import.R"))
}

```


# File reading


```{r}
labs <- dir(here::here("pilot_data"))

d <- labs %>%
  map_df(function(lab) {
    aoi_data <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/aoi_data.csv"))) 
    subjects <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/subjects.csv"))) 
    trials <- read_csv(here(paste0("pilot_data/",
                                   lab,"/processed_data/trials.csv"))) 
    datasets <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/datasets.csv")))
    
    left_join(aoi_data, subjects) %>%
      left_join(trials) %>%
      left_join(datasets) %>%
      select(lab_subject_id, lab_dataset_id, lab_trial_id, trial_id, 
             age, t, aoi, trial_num, error) %>%
      rename(subid = lab_subject_id, 
             lab = lab_dataset_id, 
             stimulus = lab_trial_id)
  })
```

# Exclusions

```{r}
# filter subjects marked error
d <- filter(d, error == F)

# print trials under 35s
group_by(d, lab, trial_id, subid) %>%
  summarise(time_range = (max(t) - min(t))/1000)  %>%
  filter(time_range <= 35) %>%
  kable(digits=2)

# filter trials under 35s (which are not complete trials)
d <- group_by(d, lab, trial_id, subid) %>%
  mutate(time_range = (max(t) - min(t))/1000) %>%
  filter(time_range > 35)

# print trial time ranges by lab
ungroup(d) %>%
  group_by(lab) %>% 
  summarise(shortest_trial=min(time_range),
            longest_trial=max(time_range)) %>%
  kable(digits=2)

# print subjects who did not complete all trials and then filter
d %>%
  group_by(lab, subid) %>%
  summarise(trials_completed = length(unique(trial_id))) %>%
  filter(trials_completed < 8) %>%
  kable(digits=2)

d <- ungroup(d) %>%
  group_by(lab, subid) %>%
  filter(length(unique(trial_id)) >= 8)
```


# Analysis

Descriptives

```{r}
d %>%
  group_by(lab, subid) %>%
  summarise(age = mean(age)) %>%
  summarise(n = n(), 
            age = mean(age)/30.25) %>%
  kable(digits = 2)
```

Anticipation plot across all trials. 

```{r}
ms <- d %>%
  group_by(t, trial_num) %>%
  summarise(target = mean(aoi == "target", na.rm=TRUE),
            distractor = mean(aoi == "distractor", na.rm=TRUE)) %>%
  gather(region, looking, target, distractor) 

ggplot(ms, aes(x = t, y = looking, col = region)) + 
  geom_line() + 
  geom_vline(xintercept = 120, col = "red", lty = 2)

```    

In the primary time period of interest

```{r}
ms <- d %>%
  group_by(t) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  geom_text(x = -4000, y = .95, group = 1, col = "black", 
            label = "Anticipation", hjust = 0) + 
  geom_text(x = 200, y = .95, group = 1, col = "black", 
            label = "Reaction", hjust = 0)
```

Now, broken down by trial.

```{r}
ms <- d %>%
  group_by(t, trial_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(filter(ms, region == "target"), 
       aes(x = t, y = looking, col = factor(trial_num))) +
  geom_point() + 
  geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  geom_text(x = -4000, y = .95, group = 1, col = "black", 
            label = "Anticipation", hjust = 0 ) + 
  geom_text(x = 200, y = .95, group = 1, col = "black", 
            label = "Reaction", hjust = 0 )
```

Summary across anticipation window.

```{r}
ms <- d %>%
  filter(t > -4000, t < 120) %>%
  group_by(lab, subid, trial_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE)) %>%
  group_by(trial_num) %>%
  langcog::multi_boot_standard(col = "target", na.rm = TRUE)


ggplot(ms, aes(x = trial_num, y = mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_line()
```
  
   
Binned for cleaner curves

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, "Trials 1-4", "Trials 5-8")) %>%
  group_by(t, block) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) +
  geom_vline(xintercept = 120, col = "black", lty = 3) + 
  annotate("text", x = -3800, y = 1, col = "black",
            label = "Anticipation", hjust = 0) +
  annotate("text", x = 200, y = 1, col = "black", 
            label = "Reaction", hjust = 0) + 
  ggthemes::scale_color_solarized(name = "Area of Interest") + 
  xlab("Time (msec)") + 
  ylab("Proportion gaze in AOI") + 
  theme(legend.position = "bottom") + 
  facet_wrap(~block)
```

And by lab:

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, 1, 2)) %>%
  group_by(t, lab, block) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) +
  facet_grid(lab~block)
```

<!-- # XY visualizations -->

<!-- First get data.  -->

<!-- ```{r} -->
<!-- xyd <- labs %>% -->
<!--   map_df(function(lab) { -->
<!--     xy_data <- read_csv(here(paste0("pilot_data/", -->
<!--                                      lab,"/processed_data/xy_data.csv")))  -->
<!--     subjects <- read_csv(here(paste0("pilot_data/", -->
<!--                                      lab,"/processed_data/subjects.csv")))  -->
<!--     trials <- read_csv(here(paste0("pilot_data/", -->
<!--                                    lab,"/processed_data/trials.csv")))  -->
<!--     datasets <- read_csv(here(paste0("pilot_data/", -->
<!--                                      lab,"/processed_data/datasets.csv"))) -->

<!--     left_join(xy_data, subjects) %>% -->
<!--       left_join(trials) %>% -->
<!--       left_join(datasets) %>% -->
<!--       select(lab_subject_id, lab_dataset_id, lab_trial_id, trial_id,  -->
<!--              age, t, x, y, trial_num, error) %>% -->
<!--       rename(subid = lab_subject_id,  -->
<!--              lab = lab_dataset_id,  -->
<!--              stimulus = lab_trial_id) -->
<!--   }) -->
<!-- ``` -->

<!-- Deal with timing in xy_data. TODO: do this re-zeroing by trial in the importing. -->

<!-- ```{r} -->
<!-- pod <- 30600 -->
<!-- xyd <- xyd %>% -->
<!--   group_by(subid, lab, trial_id) %>% -->
<!--   mutate(t = t - t[1], -->
<!--          t = t - pod) -->
<!-- ``` -->

<!-- TODO: add exclusions. -->

<!-- Used the `av` package to split video to 40fps images (just for resampling convenience.  -->


<!-- ```{r} -->
<!-- #FAM_LL_1200x900 -->
<!-- # https://stackoverflow.com/questions/42333085/how-to-fit-the-plot-over-a-background-image-in-r-and-ggplot2 -->
<!-- # start time: 27 seconds -->

<!-- screen_size <- c(1920,1080) -->
<!-- clip_size <- c(1200,900) -->

<!-- frame2time <- function (f) {  -->
<!--   ((f / 40)*1000) - pod -->
<!-- } -->

<!-- frames <- 1200:1205 -->
<!-- p <- list() -->

<!-- for (i in 1:length(frames)) { -->

<!--   frame <- frames[i] -->
<!--   time <- frame2time(frame) -->

<!--   img <- readJPEG(paste0("media/FAM_LL_1200x900/image_",  -->
<!--                          sprintf("%06.0f", frame),".jpg")) -->

<!--   g <- rasterGrob(img,  -->
<!--                   width = unit(1,"npc"),  -->
<!--                   height = unit(1, "npc"),  -->
<!--                   interpolate = FALSE) -->

<!--   plot_data <- xyd %>% -->
<!--     filter(str_detect(stimulus, "FAM_LL_1200x900*"),  -->
<!--            t > time, t < time + 25) -->

<!--   p[i] <- ggplot(data = plot_data) + -->
<!--     annotation_custom(g,  -->
<!--                       xmin = (screen_size[1] - clip_size[1])/2,  -->
<!--                       xmax = clip_size[1] + (screen_size[1] - clip_size[1])/2,  -->
<!--                       ymin = (screen_size[2] - clip_size[2])/2,  -->
<!--                       ymax = clip_size[2] + (screen_size[2] - clip_size[2])/2) +  -->
<!--     geom_point(aes(x = x,  -->
<!--                    y = screen_size[2] - y,  -->
<!--                    col = lab),  -->
<!--                alpha = 1) + -->
<!--     xlim(0,screen_size[1]) +  -->
<!--     ylim(0,screen_size[2]) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- foo <- d %>% -->
<!--   filter(str_detect(stimulus, "FAM_LL_1200x900*"),  -->
<!--          t > -4*40, t < 0) -->

<!-- foo %>% -->
<!--   group_by(lab) %>% -->
<!--   summarise(mean = mean(aoi == "target")) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- d %>% -->
<!--   filter(str_detect(stimulus, "FAM_LL_1200x900*"),  -->
<!--          t > -4*40, t < 0) %>% -->
<!--   group_by(lab) %>% -->
<!--   summarise(target = mean(aoi == "target"),  -->
<!--             distractor = mean(aoi == "distractor"),  -->
<!--             other = mean(aoi == "other"),  -->
<!--             na = mean(is.na(aoi))) -->
<!-- ``` -->

