---
title: "MB2 Pilot Analysis"
author: "The ManyBabies Analysis Team"
date: '`r format(Sys.time(), "%a %b %d %X %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
editor_options: 
  chunk_output_type: inline
---

```{r libraries}
suppressMessages(library(here))
suppressMessages(library(jpeg))
suppressMessages(library(grid))
suppressMessages(library(lmerTest))
suppressMessages(library(car))

source(here::here("helper/common.R"))
source(here("helper/preprocessing_helper.R"))

knitr::opts_chunk$set(cache = TRUE, warn = FALSE, message = FALSE)
```


# Intro

Pilot data analysis for MB2.

We can re-preprocess all of our data, this is set not to evaluate by default. In order to do this, you will need to register with Eyelink to get their binary package and then install `edfR`.

```{r, eval=FALSE}
labs <- dir(here::here("pilot_data"))

for (lab in labs) {
  print(lab)
  source(here::here("pilot_data", lab, "import_scripts", "import.R"))
}

```


# File reading

```{r}
labs <- dir(here::here("pilot_data"))

d <- labs %>%
  map_df(function(lab) {
    aoi_data <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/aoi_data.csv"))) 
    subjects <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/subjects.csv"))) 
    trials <- read_csv(here(paste0("pilot_data/",
                                   lab,"/processed_data/trials.csv"))) 
    datasets <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/datasets.csv")))
    
    left_join(aoi_data, subjects) %>%
      left_join(trials) %>%
      left_join(datasets) %>%
      select(lab_subject_id, lab_dataset_id, lab_trial_id, trial_id, 
             age, t, aoi, trial_num, error, experiment_num) %>%
      rename(subid = lab_subject_id, 
             lab = lab_dataset_id, 
             stimulus = lab_trial_id)
  })
```

# Exclusions

```{r}
d$experiment = ifelse(grepl("1a", d$experiment_num), "1a", "1b")

# exclude subject marked with any error and/or less than 8 trials
d <- d %>% 
  group_by(lab, subid, experiment) %>%
  mutate(error_subj = any(error)) %>%
      exclude_by(quo(error_subj), quiet=FALSE) 

# exclude trials under 32s (which are not complete trials)
# changed from 35s to 32 after pilot 1b because no_outcome
# trials are shorter
d <- ungroup(d) %>% 
  group_by(lab, trial_id, subid, experiment) %>%
  mutate(time_range = (max(t) - min(t))/1000) %>%
          exclude_by(quo(time_range <= 32), quiet=FALSE)

# print trial time ranges by lab
ungroup(d) %>%
  group_by(lab, experiment) %>% 
  summarise(shortest_trial=min(time_range),
            longest_trial=max(time_range)) %>%
  kable(digits=2)

# exclude subjects who did not complete 7/8 trials
d <- ungroup(d) %>% 
  group_by(lab, subid, experiment) %>%
  mutate(trials_completed = length(unique(trial_id))) %>%
            exclude_by(quo(trials_completed < 7),quiet=FALSE)

```

# Analysis

Descriptives

```{r}
d %>%
  group_by(lab, subid) %>%
  summarise(age = mean(age)) %>%
  summarise(n = n(), 
            age = mean(age)/30.25) %>%
  kable(digits = 2)
  

```

Anticipation plot across all trials. 

```{r}
ms <- d %>% 
  group_by(t, trial_num, experiment_num) %>%
  summarise(target = mean(aoi == "target", na.rm=TRUE),
            distractor = mean(aoi == "distractor", na.rm=TRUE)) %>%
  gather(region, looking, target, distractor) 

ggplot(ms, aes(x = t, y = looking, col = region)) + 
  geom_line() + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  facet_grid(experiment_num ~ .) + 
  coord_cartesian(xlim = c(-4000+120, 4120)) #only consider the 4sec window before and after POD

```    

In the primary time period of interest

```{r}
ms <- d %>%
  group_by(t, experiment_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  geom_text(x = -4000, y = .95, group = 1, col = "black", 
            label = "Anticipation", hjust = 0) + 
  geom_text(x = 200, y = .95, group = 1, col = "black", 
            label = "Reaction", hjust = 0) + 
  facet_grid(. ~ experiment_num)
```

Now, broken down by trial.
Summary across anticipation window.

```{r}
ms <- d %>%
  filter(t > -4000, t < 120) %>%
  group_by(lab, subid, trial_num, experiment_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE)) %>%
  group_by(trial_num, experiment_num) %>%
  langcog::multi_boot_standard(col = "target", na.rm = TRUE)


ggplot(ms, aes(x = trial_num, y = mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_line() + 
  facet_grid(. ~ experiment_num)
```
  
   
Binned for cleaner curves

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, "Trials 1-4", "Trials 5-8")) %>%
  group_by(t, block, experiment_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  # geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) +
  geom_vline(xintercept = 120, col = "black", lty = 3) + 
  annotate("text", x = -3800, y = 1, col = "black",
            label = "Anticipation", hjust = 0) +
  annotate("text", x = 200, y = 1, col = "black", 
            label = "Reaction", hjust = 0) + 
  ggthemes::scale_color_solarized(name = "Area of Interest") + 
  xlab("Time (msec)") + 
  ylab("Proportion gaze in AOI") + 
  theme(legend.position = "bottom") + 
  facet_wrap(experiment_num~block)
```

And by lab:

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, 1, 2)) %>%
  group_by(t, lab, block, experiment_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  # geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) +
  facet_grid(lab~block + experiment_num)
```

# Main analysis 1: First anticipatory look

Create a dataframe to identify the first look and see if the first look is >100ms

```{r, eval = FALSE}
 
# gal's approach
df_t_first_aoi <- d %>% 
  filter(., experiment_num == "pilot_1a",
         t >= -4000, t <= 120, 
         aoi %in% c("target", "distractor")) %>% 
        group_by(subid, trial_num) %>% 
  mutate(first_look_aoi = rle(aoi)$values[rle(aoi)$lengths > 4][1]) %>% # 4 consecutive timepoints looking at target or distractor is counted as first look
    ungroup() 

# short df with first looks to check
first_looks_df <- df_t_first_aoi %>% 
  select('subid','trial_num','first_look_aoi') %>% 
  group_by(subid, trial_num) %>%
  summarize(aoi = unique(first_look_aoi))



#First, create several variables that indicate first_look_time in each trial for each subject, recode aoi into dummy variable and combine string
df_t_first_aoi <- d %>% 
  filter(., experiment_num == "pilot_1a",
         t >= -4000, t <= 120, 
         aoi %in% c("target", "distractor")) %>% 
  mutate(aoi_dummy = case_when(aoi == "target" ~ 1, aoi == "distractor" ~ 0),
         subid_trial = paste0(subid, sep = "_trial_", trial_num)) %>% 
  group_by(subid, trial_num) %>% 
  mutate(first_look_time = t[1],
         diff = aoi_dummy - lag(aoi_dummy)) %>% 
  ungroup() 

#df_t_first_aoi$Mov_Avg <- zoo::rollapply(df_t_first_aoi$diff, width = 4, by = 1, FUN = mean, na.rm = TRUE, align = "left")

# head_4 <- function(df){df %>% slice(1:4)}
# 
# df_t_4 <- df_t_first_aoi %>% split(.$subid, .$trial_num) %>%
#                   map_df(head_4) %>%
#                   filter(diff != 0) %>% 
#                   mutate(subid_trial = paste0(subid, trial_num))

#unique(df_t_4$subid_trial) 
# 
# df_t_change_kids <- df_t_first_aoi %>% 
#                     mutate(subid_trial = paste0(subid, trial_num)) %>% 
#                     filter(subid_trial %in% df_t_4$subid_trial) %>% 
#                     select(subid_trial, subid, trial_num, t, first_look_time, aoi, aoi_dummy)
# 
# df_t_first_aoi <- df_t_first_aoi %>% 
#   select(subid_trial, subid, lab, stimulus, age, trial_num, t, first_look_time, aoi, aoi_dummy) %>% 
#   filter(t == first_look_time) %>% 
#   mutate(first_look_location = case_when(subid_trial == "lmu_child044" ~ 1,
#                                        subid_trial == "lmu_child111" ~ 0,
#                                        subid_trial == "lmu_child115" ~ 0,
#                                        subid_trial == "lmu_child121" ~ 1,
#                                        subid_trial == "mb2_p123" ~ 1,
#                                        subid_trial == "mb2_p164" ~ 1,
#                                        subid_trial == "mb2_p37" ~ 0,
#                                        subid_trial == "MB2_P46" ~ 0,
#                                        subid_trial == "MB2_P56" ~ 0,
#                                        subid_trial == "MB2-108" ~ 0,
#                                        subid_trial == "MB2-117" ~ 1,
#                                        subid_trial == "MB2-124" ~ 1,
#                                        subid_trial == "MB2-126" ~ 1,
#                                        subid_trial == "mb2p067" ~ 1,
#                                        subid_trial == "mb2p103" ~ 1,
#                                        subid_trial == "mb2p114" ~ NA_real_,
#                                        subid_trial == "mb2p126" ~ 0,
#                                        subid_trial == "mb2p127" ~ 1,
#                                        TRUE ~ aoi_dummy)) %>% 
#   filter(!is.na(first_look_location))
```

## Data visualization across different test trials

```{r, eval = FALSE}
ggplot(df_t_first_aoi, aes(x = first_look_location)) + 
  geom_bar() + 
  facet_wrap(.~trial_num, ncol = 4)
```

## Descriptive stats

mean and sd of first look location in different trials. All numbers seem to be above 50%

```{r, eval = FALSE}
df_t_first_aoi %>% 
  select(trial_num, first_look_location) %>% 
  group_by(trial_num) %>% 
  summarize(number_of_kids_each_trial = n(),
            mean(first_look_location),
            sd(first_look_location))
```

## Mixed-level analysis: First look location

```{r first_look_analysis, results = "verbatim", eval = FALSE}
first_look_logistic <- glmer(first_look_location ~ trial_num + (1|subid), data = df_t_first_aoi, family = "binomial")

summary(first_look_logistic)
```

Mean level. 

```{r, eval = FALSE}
mean(df_t_first_aoi$first_look_location)
```




# Main analysis 2: Differential analysis 
This analysis explores whether kids looked at the target more than distractor during anticipatory period. 

## Data visualization across different test trials
```{r}
ms_proportion_trials <- d %>%
  group_by(t, trial_num, experiment_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  mutate(proportion_to_target = target / (target + distractor)) %>% 
  filter(t >= -2120 & t <= 2120)


ggplot(ms_proportion_trials, 
       aes(x = t, y = proportion_to_target)) +
  geom_point(alpha = 0.3) + 
  ylim(0,1) + 
  # geom_smooth(span = 2, se = FALSE) + 
  xlim(-2120, 2120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  geom_text(x = -2000, y = .95, group = 1, col = "black", 
            label = "Anticipation", hjust = 0 ) + 
  geom_text(x = 200, y = .95, group = 1, col = "black", 
            label = "Reaction", hjust = 0 )+
  facet_wrap(experiment_num~trial_num, ncol = 4)   
```

Create data-set for the mixed-level analysis
```{r}
ms_proportion_trials <- d %>%
  filter (t >= -4000 & t <= 120) %>% 
  group_by(experiment_num, trial_num, subid, lab) %>%
  summarise(mean_target = mean(aoi == "target", na.rm = TRUE),
            sem_target = sd(aoi == "target", na.rm = TRUE) / sqrt(length(aoi == "target")),
            mean_distractor = mean(aoi == "distractor", na.rm = TRUE), 
            sem_distractor = sd(aoi == "distractor", na.rm = TRUE) / sqrt(length(aoi == "distractor")),
            up_ci_target = mean_target + (sem_target * 1.96),
            low_ci_target = mean_target - (sem_target * 1.96),
            up_ci_distractor = mean_distractor + (sem_distractor * 1.96),
            low_ci_distractor = mean_distractor - (sem_distractor * 1.96)) %>% 
  mutate(proportion_to_target = mean_target / (mean_target + mean_distractor))
```

## Logistic Mixed-level analysis during the pre-disambiguation period (-2120 to 120 window)

### compare pilot 1a (trial 1 to 4) and pilot 1b outcome
```{r mixed-level logistic analysis}
d_2120_window_1a_1b_outcome <- d %>% 
  filter(t >= -2120, t <= 120, 
         experiment_num %in% c("pilot_1a", "pilot_1b_outcome"), 
         trial_num <5,
         aoi != "other") %>%
  mutate(aoi_dummy = case_when(aoi == "target" ~ 1, 
                               aoi == "distractor" ~ 0))

ls_target_2120_1a_1b_outcome <- glmer(aoi_dummy ~ trial_num + experiment_num + (trial_num|subid), 
                                     data = d_2120_window_1a_1b_outcome, family = "binomial")
summary(ls_target_2120_1a_1b_outcome)
```

### only focus on pilot 1b non outcome
```{r}
d_2120_window_1b_no_outcome <- d %>% 
  filter(t >= -2120, t <= 120, 
         experiment_num == "pilot_1b_no_outcome",
         aoi != "other") %>%
  mutate(aoi_dummy = case_when(aoi == "target" ~ 1, 
                               aoi == "distractor" ~ 0))

ls_target_2120_1b_no_outcome <- glmer(aoi_dummy ~ trial_num + (trial_num|subid), 
                                     data = d_2120_window_1b_no_outcome, family = "binomial")
summary(ls_target_2120_1b_no_outcome)
```

## Logistic Mixed-level analysis during the poste-disambiguation period (0 to 2120), compare pilot 1b outcome vs no-outcome
```{r}
d_2120_window_1b <- d %>% 
  filter(t >= 0, t <= 2120, 
         experiment_num != "pilot_1a",
         aoi != "other") %>%
  mutate(aoi_dummy = case_when(aoi == "target" ~ 1, 
                               aoi == "distractor" ~ 0))

ls_target_2120_1b <- glmer(aoi_dummy ~ trial_num + experiment_num + (trial_num|subid), 
                                     data = d_2120_window_1b, family = "binomial")
summary(ls_target_2120_1b)
```

```{r prop looking, eval = FALSE}

# df_pilot_1a_b_trial1to4 <- ms_proportion_trials %>% filter(experiment_num != "pilot_1b_no_outcome", trial_num <5)
# 
# 
# prop_model_1a_b_trial_1to4 <- lmer(proportion_to_target ~ experiment_num + trial_num + (1|subid), data = df_pilot_1a_b_trial1to4)
# summary(prop_model_1a_b_trial_1to4) 

## Linear hypothesis test to see if the intercept of the prop_model is signficantly higher than chance level (0.5)
 
# linearHypothesis(prop_model, "(Intercept) = 0.5")

# the linear hypothesis test is also confirmed by calculating the z score of this intercept, I used the coefficient and the sd of the random intercept
# z_intercept <- 0.7525/0.066 #much higher than 1.96
```
