---
title: "MB2 Pilot Analysis"
author: "The ManyBabies Analysis Team"
date: '`r format(Sys.time(), "%a %b %d %X %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
editor_options: 
  chunk_output_type: inline
---

```{r libraries}
suppressMessages(library(here))
suppressMessages(library(jpeg))
suppressMessages(library(grid))
suppressMessages(library(lmerTest))
suppressMessages(library(car))

source(here::here("helper/common.R"))
source(here("helper/preprocessing_helper.R"))

knitr::opts_chunk$set(cache = TRUE, warn = FALSE, message = FALSE)
```


# Intro

Pilot data analysis for MB2.

We can re-preprocess all of our data, this is set not to evaluate by default. In order to do this, you will need to register with Eyelink to get their binary package and then install `edfR`.

```{r, eval=FALSE}
labs <- dir(here::here("pilot_data"))

for (lab in labs) {
  print(lab)
  source(here::here("pilot_data", lab, "import_scripts", "import.R"))
}

```


# File reading

```{r}
labs <- dir(here::here("pilot_data"))
labs = labs[!grepl("1b", labs)]
labs = append(labs, "pilot_1b_copenhagen")

d <- labs %>%
  map_df(function(lab) {
    aoi_data <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/aoi_data.csv"))) 
    subjects <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/subjects.csv"))) 
    trials <- read_csv(here(paste0("pilot_data/",
                                   lab,"/processed_data/trials.csv"))) 
    datasets <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/datasets.csv")))
    
    left_join(aoi_data, subjects) %>%
      left_join(trials) %>%
      left_join(datasets) %>%
      mutate(experiment_num = ifelse(dataset_id < 7, "1a", "1b")) %>%
      select(lab_subject_id, lab_dataset_id, lab_trial_id, trial_id, 
             age, t, aoi, trial_num, error, experiment_num) %>%
      rename(subid = lab_subject_id, 
             lab = lab_dataset_id, 
             stimulus = lab_trial_id)
  })
```

# Exclusions

```{r}
# exclude subject marked with any error and/or less than 8 trials
d <- d %>% 
  group_by(lab, subid) %>%
  mutate(error_subj = any(error)) %>%
      exclude_by(quo(error_subj), quiet=FALSE) 

# exclude trials under 35s (which are not complete trials)
d <- ungroup(d) %>% 
  group_by(lab, trial_id, subid) %>%
  mutate(time_range = (max(t) - min(t))/1000) %>%
          exclude_by(quo(time_range <= 35), quiet=FALSE)

# print trial time ranges by lab
ungroup(d) %>%
  group_by(lab) %>% 
  summarise(shortest_trial=min(time_range),
            longest_trial=max(time_range)) %>%
  kable(digits=2)

# exclude subjects which did not complete all 8 trials
d <- ungroup(d) %>% 
  group_by(lab, subid) %>%
  mutate(trials_completed = length(unique(trial_id))) %>%
            exclude_by(quo(trials_completed < 8),quiet=FALSE)

```

# Analysis

Descriptives

```{r}
d %>%
  group_by(lab, subid) %>%
  summarise(age = mean(age)) %>%
  summarise(n = n(), 
            age = mean(age)/30.25) %>%
  kable(digits = 2)
  

```

Anticipation plot across all trials. 

```{r}
ms <- d %>% 
  group_by(t, trial_num, experiment_num) %>%
  summarise(target = mean(aoi == "target", na.rm=TRUE),
            distractor = mean(aoi == "distractor", na.rm=TRUE)) %>%
  gather(region, looking, target, distractor) 

ggplot(ms, aes(x = t, y = looking, col = region)) + 
  geom_line() + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  facet_grid(experiment_num ~ .)

```    

In the primary time period of interest

```{r}
ms <- d %>%
  group_by(t, experiment_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  geom_text(x = -4000, y = .95, group = 1, col = "black", 
            label = "Anticipation", hjust = 0) + 
  geom_text(x = 200, y = .95, group = 1, col = "black", 
            label = "Reaction", hjust = 0) + 
  facet_grid(. ~ experiment_num)
```

Now, broken down by trial.
Summary across anticipation window.

```{r}
ms <- d %>%
  filter(t > -4000, t < 120) %>%
  group_by(lab, subid, trial_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE)) %>%
  group_by(trial_num) %>%
  langcog::multi_boot_standard(col = "target", na.rm = TRUE)


ggplot(ms, aes(x = trial_num, y = mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_line()
```
  
   
Binned for cleaner curves

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, "Trials 1-4", "Trials 5-8")) %>%
  group_by(t, block) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  # geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) +
  geom_vline(xintercept = 120, col = "black", lty = 3) + 
  annotate("text", x = -3800, y = 1, col = "black",
            label = "Anticipation", hjust = 0) +
  annotate("text", x = 200, y = 1, col = "black", 
            label = "Reaction", hjust = 0) + 
  ggthemes::scale_color_solarized(name = "Area of Interest") + 
  xlab("Time (msec)") + 
  ylab("Proportion gaze in AOI") + 
  theme(legend.position = "bottom") + 
  facet_wrap(~block)
```

And by lab:

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, 1, 2)) %>%
  group_by(t, lab, block) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  gather(region, looking, target, distractor) 
  
ggplot(ms, aes(x = t, y = looking, col = region)) +
  geom_point() + 
  # geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) +
  facet_grid(lab~block)
```

# Main analysis 1: First anticipatory look

First, create a function that extract the time stamp of first aoi.

```{r}
t_first_aoi <- function(df){
  
  df <- df %>% 
    filter(t >= -4000, t <= 120, aoi == c("target", "distractor")) 
  
 df = df %>% group_by(subid, trial_num) %>% mutate(first_look_time = t[1])
  
  return(df)
}
```

Second, create a dataframe to identify the first look and see if the first look is >100ms

Note that this is done ad-hoc for a number of participants. TODO - cleanup!

```{r}
df_t_first_aoi <- d %>% split(.$subid, .$trial_num) %>% 
  map_df(t_first_aoi) %>% 
  mutate(aoi_dummy = case_when(aoi == "target" ~ 1, aoi == "distractor" ~ 0),
         subid_trial = paste0(subid, trial_num)) 

df_t_first_aoi <- df_t_first_aoi %>% 
                  group_by(subid, trial_num) %>% 
                  mutate(diff = aoi_dummy - lag(aoi_dummy))

head_4 <- function(df){df %>% slice(1:4)}

df_t_4 <- df_t_first_aoi %>% split(.$subid, .$trial_num) %>%
                  map_df(head_4) %>%
                  filter(diff != 0) %>% 
                  mutate(subid_trial = paste0(subid, trial_num))

unique(df_t_4$subid_trial) 

df_t_change_kids <- df_t_first_aoi %>% 
                    mutate(subid_trial = paste0(subid, trial_num)) %>% 
                    filter(subid_trial %in% df_t_4$subid_trial) %>% 
                    select(subid_trial, subid, trial_num, t, first_look_time, aoi, aoi_dummy)

df_t_first_aoi <- df_t_first_aoi %>% 
  select(subid_trial, subid, lab, stimulus, age, trial_num, t, first_look_time, aoi, aoi_dummy) %>% 
  filter(t == first_look_time) %>% 
  mutate(first_look_location = case_when(subid_trial == "lmu_child044" ~ 1,
                                       subid_trial == "lmu_child111" ~ 0,
                                       subid_trial == "lmu_child115" ~ 0,
                                       subid_trial == "lmu_child121" ~ 1,
                                       subid_trial == "mb2_p123" ~ 1,
                                       subid_trial == "mb2_p164" ~ 1,
                                       subid_trial == "mb2_p37" ~ 0,
                                       subid_trial == "MB2_P46" ~ 0,
                                       subid_trial == "MB2_P56" ~ 0,
                                       subid_trial == "MB2-108" ~ 0,
                                       subid_trial == "MB2-117" ~ 1,
                                       subid_trial == "MB2-124" ~ 1,
                                       subid_trial == "MB2-126" ~ 1,
                                       subid_trial == "mb2p067" ~ 1,
                                       subid_trial == "mb2p103" ~ 1,
                                       subid_trial == "mb2p114" ~ NA_real_,
                                       subid_trial == "mb2p126" ~ 0,
                                       subid_trial == "mb2p127" ~ 1,
                                       TRUE ~ aoi_dummy)) %>% 
  filter(!is.na(first_look_location))
```

## Data visualization across different test trials

```{r}
ggplot(df_t_first_aoi, aes(x = first_look_location)) + 
  geom_bar() + 
  facet_wrap(.~trial_num, ncol = 4)
```

## Descriptive stats

mean and sd of first look location in different trials. All numbers seem to be above 50%

```{r}
df_t_first_aoi %>% 
  select(trial_num, first_look_location) %>% 
  group_by(trial_num) %>% 
  summarize(number_of_kids_each_trial = n(),
            mean(first_look_location),
            sd(first_look_location))
```

## Mixed-level analysis: First look location

```{r first_look_analysis, results = "verbatim"}
first_look_logistic <- glmer(first_look_location ~ trial_num + (1|subid), data = df_t_first_aoi, family = "binomial")

summary(first_look_logistic)
```

Mean level. 

```{r}
mean(df_t_first_aoi$first_look_location)
```




# Main analysis 2: Differential analysis 

## Data visualization across different test trials
```{r}
ms_proportion_trials <- d %>%
  group_by(t, trial_num) %>%
  summarise(target = mean(aoi == "target", na.rm = TRUE),
            distractor = mean(aoi == "distractor", na.rm = TRUE)) %>%
  mutate(proportion_to_target = target / (target + distractor)) %>% 
  filter(t >= -4000 & t <= 120+ 4000)


ggplot(ms_proportion_trials, 
       aes(x = t, y = proportion_to_target)) +
  geom_point(alpha = 0.3) + 
  ylim(0,1) + 
  # geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  geom_text(x = -4000, y = .95, group = 1, col = "black", 
            label = "Anticipation", hjust = 0 ) + 
  geom_text(x = 200, y = .95, group = 1, col = "black", 
            label = "Reaction", hjust = 0 )+
  facet_wrap(.~trial_num, ncol = 4)   
```

Create data-set for the mixed-level analysis
```{r}
ms_proportion_trials <- d %>%
  filter (t >= -4000 & t <= 120) %>% 
  group_by(trial_num, subid, lab) %>%
  summarise(mean_target = mean(aoi == "target", na.rm = TRUE),
            sem_target = sd(aoi == "target", na.rm = TRUE) / sqrt(length(!is.na(aoi))),
            mean_distractor = mean(aoi == "distractor", na.rm = TRUE), 
            sem_distractor = sd(aoi == "distractor", na.rm = TRUE) / sqrt(length(!is.na(aoi))),
            up_ci_target = mean_target + (sem_target * 1.96),
            low_ci_target = mean_target - (sem_target * 1.96),
            up_ci_distractor = mean_distractor + (sem_distractor * 1.96),
            low_ci_distractor = mean_distractor - (sem_distractor * 1.96)) %>% 
  mutate(proportion_to_target = mean_target / (mean_target + mean_distractor))
```

## Mixed-level analysis for diff-score analysis

Note that technically we had 68 participants, but this analysis was based on 63 kids because not all kids looked at either target/distractor between -4000 ms to 120 ms (i.e., they either looked away (missing data) or looked at other parts of the screen (other))


```{r mixed-level analysis}
# Lmer_originally, I tried the following but it didn't converge:  lmer(proportion_to_target ~ trial_num + + (1|lab) + (trial_num|subid), data = ms_proportion_trials), so I changed the model to a simpler one below
prop_model <- lmer(proportion_to_target ~ trial_num + (1|subid), data = ms_proportion_trials)
summary(prop_model) 



# did a linear hypothesis test to see if the intercept of the prop_model is signficantly higher than chance level (0.5)
linearHypothesis(prop_model, "(Intercept) = 0.5")

# the linear hypothesis test is also confirmed by calculating the z score of this intercept, I used the coefficient and the sd of the random intercept
z_intercept <- 0.7525/0.066 #much higher than 1.96,
```
