---
title: "MB2 Pilot Analysis"
author: "The ManyBabies Analysis Team"
date: '`r format(Sys.time(), "%a %b %d %X %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
editor_options: 
  chunk_output_type: inline
---

```{r libraries}
suppressMessages(library(here))
suppressMessages(library(jpeg))
suppressMessages(library(grid))
suppressMessages(library(lmerTest))
suppressMessages(library(car))

source(here::here("helper/common.R"))
source(here("helper/preprocessing_helper.R"))

knitr::opts_chunk$set(cache = TRUE, warn = FALSE, message = FALSE)
```


# Intro

Pilot data analysis for MB2.

We can re-preprocess all of our data, this is set not to evaluate by default. In order to do this, you will need to register with Eyelink to get their binary package and then install `edfR`.

```{r, eval=FALSE}
labs <- dir(here::here("pilot_data"))

for (lab in labs) {
  print(lab)
  source(here::here("pilot_data", lab, "import_scripts", "import.R"))
}

```


# File reading

```{r}
labs <- dir(here::here("pilot_data"))

d <- labs %>%
  map_df(function(lab) {
    aoi_data <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/aoi_data.csv"))) 
    subjects <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/subjects.csv"))) 
    trials <- read_csv(here(paste0("pilot_data/",
                                   lab,"/processed_data/trials.csv"))) 
    datasets <- read_csv(here(paste0("pilot_data/",
                                     lab,"/processed_data/datasets.csv")))
    
    left_join(aoi_data, subjects) %>%
      left_join(trials) %>%
      left_join(datasets) %>%
      select(lab_subject_id, lab_dataset_id, lab_trial_id, trial_id, 
             age, t, aoi, trial_num, error, experiment_num) %>%
      rename(subid = lab_subject_id, 
             lab = lab_dataset_id, 
             stimulus = lab_trial_id)
  })
```

# Exclusions

```{r}
d$experiment = ifelse(grepl("1a", d$experiment_num), "1a", "1b")

# exclude subject marked with any error and/or less than 8 trials
d <- d %>% 
  group_by(lab, subid, experiment) %>%
  mutate(error_subj = any(error)) %>%
      exclude_by(quo(error_subj), quiet=FALSE) 

# exclude trials under 32s (which are not complete trials)
# changed from 35s to 32 after pilot 1b because no_outcome
# trials are shorter
d <- ungroup(d) %>% 
  group_by(lab, trial_id, subid, experiment) %>%
  mutate(time_range = (max(t) - min(t))/1000) %>%
          exclude_by(quo(time_range <= 32), quiet=FALSE)

# print trial time ranges by lab
ungroup(d) %>%
  group_by(lab, experiment) %>% 
  summarise(shortest_trial=min(time_range),
            longest_trial=max(time_range)) %>%
  kable(digits=2)

# exclude subjects who did not complete 7/8 trials
d <- ungroup(d) %>% 
  group_by(lab, subid, experiment) %>%
  mutate(trials_completed = length(unique(trial_id))) %>%
           exclude_by(quo(trials_completed < 7),quiet=FALSE) %>% 
  ungroup(d) %>% 
mutate(subid = paste(subid, lab, experiment, sep="_"))

```

# Analysis

Descriptives

```{r}
d %>%
  group_by(experiment, lab, subid) %>%
  summarise(age = mean(age)) %>%
  summarise(n = n(), 
            age = mean(age)/30.25) %>%
  kable(digits = 2)
  

```

The whole time period.

```{r}
ms <- d %>% 
  group_by(t, trial_num, experiment_num) %>%
  summarise(target_exit = mean(aoi == "target_exit", na.rm=TRUE),
            target_box = mean(aoi == "target_box", na.rm=TRUE),
            distractor_exit = mean(aoi == "distractor_exit", na.rm=TRUE),
            distractor_box = mean(aoi == "distractor_box", na.rm=TRUE),
            window_window = mean(aoi == "window_window", na.rm=TRUE)) %>%
  gather(region, looking, target_exit, target_box, distractor_exit, 
         distractor_box, window_window) %>% 
  mutate(areas = case_when(region %in% c("target_exit", "distractor_exit") ~ "exit",
         region %in% c("target_box", "distractor_box") ~ "box",
         region == "window_window" ~"window"))  
   

for (i in unique(ms$experiment_num)) {
  print(ggplot(data = filter(ms, experiment_num == i), aes(x = t, y = looking, col = region)) + 
  geom_line() + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  facet_grid( areas ~ .) + 
  theme_bw(12) + 
      theme(legend.position = "bottom") + 
    ggtitle(i) #only consider the 4sec window before and after POD
  )
}
```    


Just the means (single lines).

```{r}
ms <- d %>% 
  group_by(t, experiment_num) %>%
  summarise(target_exit = mean(aoi == "target_exit", na.rm=TRUE),
            target_box = mean(aoi == "target_box", na.rm=TRUE),
            distractor_exit = mean(aoi == "distractor_exit", na.rm=TRUE),
            distractor_box = mean(aoi == "distractor_box", na.rm=TRUE),
            window_window = mean(aoi == "window_window", na.rm=TRUE)) %>%
  gather(region, looking, target_exit, target_box, distractor_exit, 
         distractor_box, window_window) %>% 
  mutate(areas = case_when(region %in% c("target_exit", "distractor_exit") ~ "exit",
         region %in% c("target_box", "distractor_box") ~ "box",
         region == "window_window" ~"window"),
         region_type = case_when(grepl("target", region) ~ "target", 
                                 grepl("window", region) ~ "window",
                                 TRUE ~ "distractor")) %>%
  filter(is.na(experiment_num) == F)
   

  print(ggplot(data = ms, aes(x = t, y = looking, col = region_type, group=region)) + 
  geom_line() + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  facet_grid(experiment_num~ areas) + 
  coord_cartesian(xlim = c(-4000+120, 4120)) +
  theme_bw(14)   )
```    

Just the time period of interest

```{r}
ms <- d %>% 
  group_by(t, trial_num, experiment_num) %>%
  summarise(target_exit = mean(aoi == "target_exit", na.rm=TRUE),
            target_box = mean(aoi == "target_box", na.rm=TRUE),
            distractor_exit = mean(aoi == "distractor_exit", na.rm=TRUE),
            distractor_box = mean(aoi == "distractor_box", na.rm=TRUE),
            window_window = mean(aoi == "window_window", na.rm=TRUE)) %>%
  gather(region, looking, target_exit, target_box, distractor_exit, 
         distractor_box, window_window) %>% 
  mutate(areas = case_when(region %in% c("target_exit", "distractor_exit") ~ "exit",
         region %in% c("target_box", "distractor_box") ~ "box",
         region == "window_window" ~"window"))  
   

for (i in unique(ms$experiment_num)) {
  print(ggplot(data = filter(ms, experiment_num == i), aes(x = t, y = looking, col = region)) + 
  geom_line() + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  facet_grid(areas ~ .) + 
  coord_cartesian(xlim = c(-4000+120, 4120)) +
  theme_bw(12) + 
      theme(legend.position = "bottom") + 
    ggtitle(i) #only consider the 4sec window before and after POD
  )
}
```    


Now do the analysis using "big AOIs" by combining all targets and all distractors.
```{r}

ms <- d %>% 
  group_by(t, trial_num, experiment_num) %>%
  summarise(target = mean(grepl("target", aoi), na.rm=TRUE),
            distractor = mean(grepl("distractor", aoi), na.rm=TRUE)
            ) %>%
  gather(region, looking, target, distractor) 

ggplot(ms, aes(x = t, y = looking, col = region)) + 
  geom_line() + 
  geom_vline(xintercept = 120, col = "red", lty = 2) + 
  facet_grid(experiment_num ~ .) + 
  coord_cartesian(xlim = c(-4000+120, 4120)) 
```
   
Binned for cleaner curves

```{r}
ms <- d %>%
  mutate(block = ifelse(trial_num < 5, "Trials 1-4", "Trials 5-8")) %>%
  group_by(t, block, experiment_num) %>%
  summarise(target_exit = mean(aoi == "target_exit", na.rm=TRUE),
            target_box = mean(aoi == "target_box", na.rm=TRUE),
            distractor_exit = mean(aoi == "distractor_exit", na.rm=TRUE),
            distractor_box = mean(aoi == "distractor_box", na.rm=TRUE),
            window_window = mean(aoi == "window_window", na.rm=TRUE)) %>%
  gather(region, looking, target_exit, target_box, distractor_exit, distractor_box, window_window)  %>%
  mutate(areas = case_when(region %in% c("target_exit", "distractor_exit") ~ "exit",
         region %in% c("target_box", "distractor_box") ~ "box",
         region == "window_window" ~"window"),
         id = paste(experiment_num, block))  

  
for (i in unique(ms$id)) { print(
  ggplot(filter(ms, id == i), aes(x = t, y = looking, col = region)) +
  geom_point() + 
  # geom_smooth(span = 2, se = FALSE) + 
  xlim(-4000 + 120, 4000 + 120) +
  geom_vline(xintercept = 120, col = "black", lty = 3) + 
  annotate("text", x = -3800, y = 1, col = "black",
            label = "Anticipation", hjust = 0) +
  annotate("text", x = 200, y = 1, col = "black", 
            label = "Reaction", hjust = 0) + 
  ggthemes::scale_color_solarized(name = "Area of Interest") + 
  xlab("Time (msec)") + 
  ylab("Proportion gaze in AOI") + 
  theme_bw() + 
  theme(legend.position = "bottom") + 
  facet_wrap(areas ~block) + 
    ggtitle(i)
)
}
```
